---
title: "Social Status, Liberalization and Attitudes toward Redistribution"
output:
  html_document:
    df_print: paged
---

"Social Status, Liberalization and Attitudes toward Redistribution"

## ISSP Data

Social Inequality, Cumulation (1987, 1992, 1999, 2009 & 2009)
Social Inequality, 2019
Environment (XXXX, XXXX & XXXX)
$~$
$~$


#### **Nate Breznau, Lisa Heukamp & Hung H.V. Nguyen**
#### **University of Bremen**

_____________________________________________________________________________

$~$
$~$



#### User Notes:

*1. DATA*

All files available from GESIS, ZACAT for download

We should cite properly each file

ISSP Research Group (2021): International Social Survey Programme: Social Inequality V - ISSP 2019. GESIS Data Archive, Cologne. ZA7600 Data file Version 1.0.0, https://doi.org/10.4232/1.13599

*1.A. Social Inequality*

ISSP SI combined file "ZA5890_v1-0-0.dta" used, supplemented by "ZA5891_v1-1-0.dta"

Ireland 1987 added manually "ZA1306_v1-0-0"
Netherlands 1987 added manually "ZA1689.dta" (subset to country == 7)
Denmark 1999 added manually "ZA3562_v1-0-0.dta"
Ireland 1999 added manually "ZA3613_v1-0-0.dta"
Netherlands 2009 added manually "ZA5995_v1-0-0.dta"

* Spain 1992 not enough demographic variables, Brazil 1999 methodological problems

*1.B. Environment*



Notes:


--- AWAITING SOLUTIONS ---

A. nl87 and ie87 cannot be integrated into the socin file, eeds occupation recoding before integrating but the categories are not compatible.

C. There are values of 11 in the socin$wrkst variable, these are probably from a country-specific question and need to be checked

E. We should include the other income differences question for all surveys where it is available, Nate did this for the cumulative file so far as *inclarge*

F. There are still values that fall outside of 0-5 in *incdiff* and *inclarge*
=======
   
   
   
--- DONE ---   
   
   HUNG - can you follow my coding schemes for 2-digit ISCO and apply them to mothers and fathers in Australia 1987, Italy 87 & 92 & env93, Great Britain 87 & 92 & env93, & Poland 87 please? You will find the hand recodes in the code chunk 'isco88_2'. I haven't finished coding the other countries into 2-digit isco, will finish at some point, although we have most by now. - DONE
   
   HUNG - we need to get spouse isco and spouse isco88_2digit, can you please add these everywhere? please name them spisco88 and spisco88_2digit. Of course for many countries there will be missing spisco88 in the earlier surveys, but spouse isco will be really important in determining the status of a housewife/partner. - DONE

D. I changed the variable 'year' to reflect the actual year when the survey was fielded in each country - sometimes it is not the same as 'wave', but having the year accurate as possible makes it better for merging in macro data. 

E. Made a variable 'reduce' that is = to 'incdiff' but has 9 recoded into NA and has 8 recoded into neutral, also reversed the coding so that higher values = more agreement

F. Recoded 'wrkst' so that they matched across all surveys (not just full-time, part-time, less than part time). Env00 uses a slightly different list than the others. Now wrkst doesn't have value "4". 

G. Mistake with Australia - it should not have ISCO68 in env93, it is isco88. this explains why so many values go tdropped in the conversion

--- DONE ---




--- TO BE EXECUTED ---

B. Need to use the supplementary file to divide East and West Germany at some point. Or maybe not. If we think of Germany as a political unit where policy change is or is not possible, it makes sense to use all of Germany (whatever that means at the time) to look for majority constellations. 

C. We should see if there is any way to remove the NA from child, maybe they can safely be recoded to zero? 


--- TO BE EXECUTED ---



## SETUP

```{r, include = F}
# optional fast way to clear environment
rm(list = ls())
```


```{r setup, include=FALSE}

library(pacman)

pacman::p_load("tidyverse","knitr","haven","car","plyr","e1071","stargazer","lavaan","kableExtra","MASS","glm.predict","brant", "semTools", "tidylog", "countrycode", "Hmisc", "ineq")

#remotes::install_github("DiogoFerrari/occupar")
#remotes::install_github("pdparker/isco88conversion")
library(occupar, isco88conversion)

# We don't want to see messages in the final document
knitr::opts_chunk$set(message = F)

# worked up in /data/ISSP_prep.R

load(here::here("data","issp.Rdata"))

```



## Data transformation - Social Inequality 

```{r socin, include = TRUE, warning=F}
# Cumulative files
## General variables
colnames(socin) <- tolower(colnames(socin))

socin <- socin %>% 
  mutate(
     incdiff = v33,
     inclarge = v32,
     cntry = v5,
     year = v4,
     wave = v4,
     female = ifelse(sex == 9, NA, sex - 1), # female = 1
     ageC = ifelse(age > 75, 75, age), # also a continuous measure
     age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,        # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
     married = case_when( # married = 1. Note: using if_else will confound NA with not married (0), make sure life partners are coded as married
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
     ),
     educyrs = case_when(                 # years in school, trim at 23 years
       .$educyrs > 22 & .$educyrs < 95 ~ 23, # 23 = 23+ years in school
       .$educyrs == 95 ~ 8, # still in school
       .$educyrs == 96 ~ 13,
       .$educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(as.character(.$educyrs))
     ),
     #household income and personal earnings are not comparable: sometimes monthly, sometimes yearly, 
     #in different national currency and not adjusted for inflations
     child = case_when(
       hhcycle %in% c(2,3,4,6,7,8,10,11,12,14,16,18,20,22,24,26,28)  ~ 1,
       hhcycle %in% c(1,5,9,13,15,17,19,21,23,25,27,95) ~ 0,
       TRUE ~ NA_real_
     ),
     union = case_when( # 1 = member
       union == 1 ~ 1,
       union == 2 ~ 0,
       TRUE ~ NA_real_
     ),
     sparent = case_when(   # single parent
       hhcycle %in% c(2,3,4) ~ 1, # if one is married but living away from their partner (and raising children), count as single parent?
       hhcycle %in% c(1,5:95) ~ 0,
       TRUE ~ NA_real_
     ),
     wrkst = ifelse(wrkst == 4, 8, wrkst), # recode helping fam member into housework category to make compatible with environment category
     wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs) # trim workhrs
  )
# integrate hhcycle from socin2 (US92)
socin2 <- socin2 %>%
  mutate(
    child2 = case_when(
      HCY_US92 %in% c(3,11,13,15,16,18) ~ 1, 
      HCY_US92 %in% c(1,2,4,5,6,7) ~ 0,
      TRUE ~ NA_real_
    )
  )

socin$hhcycle_us92 <- socin2$child2 
socin$child <- coalesce(socin$child, socin$hhcycle_us92)

## Income
# Is coded in local currency and this really skews the standardization process. Recode into local deciles

# Respondent income

temp <- dplyr::select(socin2, AT_RIN87:US_RIN09)
socin <- bind_cols(socin,temp)

socin$rincZ <- rowMeans(socin[,which(names(socin)=="AT_RIN87"):which(names(socin)=="US_RIN09")], na.rm = T)

socin$rincZ <- ifelse(socin$rincZ=="NaN",NA,socin$rincZ)

# Take the orignal incomes to compute Gini's coefficient

socin$rincO <- rowMeans(socin[,which(names(socin)=="AT_RIN87"):which(names(socin)=="US_RIN09")], na.rm = T)
socin$rincO <- ifelse(socin$rincO=="NaN",NA,socin$rincO)


## Household income

temp <- dplyr::select(socin2, AT_INC87:US_INC09)
socin <- cbind(socin,temp)
socin$hincZ = rowMeans(socin[,which(names(socin)=="AT_INC87"):which(names(socin)=="US_INC09")], na.rm = T)
socin$hincZ = ifelse(socin$hincZ=="NaN",NA,socin$hincZ)

# Standarize by country and year

socin <- socin %>%
  group_by(v4,v5) %>%
  mutate(rincZ = scale(rincZ),
         hincZ = scale(hincZ)) %>%
  ungroup()
# Think about ISCED for education (see Schneider's work). #Hung# Two problems: (1) we would have to code each country-year separately; (2) more importantly, many countries don't record degrees higher than bachelor (master and doctoral), which are 7 and 8 in the ISCED 2011 coding scheme. For the mean time, I propose we use the variable degree instead.
```

## Occupation Coding Harmonization

#### 1987

NET - handcodes [
01 Manager 10 and more employees
02 Manager 9 and less employees
03 Professional
04 Farmer
05 Higher employee
06 Intermediate employee
07 Lower employee
08 Skilled labourer
09 Unskilled labourer
]


#### 1992
GB - SOC
I - Italian Occupation Code
S - Nordic Occupation Code NYK


#### 1999


#### 2009

#### ISCO88 2-digit is all we need to determine the social groups of Schwander & Haeuserman

1	Managers
11	Chief Executives, Senior Officials and Legislators
12	Administrative and Commercial Managers
13	Production and Specialized Services Managers
14	Hospitality, Retail and Other Services Managers

2	Professionals
21	Science and Engineering Professionals
22	Health Professionals
23	Teaching Professionals
24	Business and Administration Professionals
25	Information and Communications Technology Professionals
26	Legal, Social and Cultural Professionals
  
3	Technicians and Associate Professionals
31	Science and Engineering Associate Professionals
32	Health Associate Professionals
33	Business and Administration Associate Professionals
34	Legal, Social, Cultural and Related Associate Professionals
35	Information and Communications Technicians

4	Clerical Support Workers
41	General and Keyboard Clerks
42	Customer Services Clerks
43	Numerical and Material Recording Clerks
44	Other Clerical Support Workers

5	Services and Sales Workers
51	Personal Services Workers
52	Sales Workers
53	Personal Care Workers
54	Protective Services Workers


6	Skilled Agricultural, Forestry and Fishery Workers
61	Market-oriented Skilled Agricultural Workers
62	Market-oriented Skilled Forestry, Fishery and Hunting Workers
63	Subsistence Farmers, Fishers, Hunters and Gatherers

7	Craft and Related Trades Workers
71	Building and Related Trades Workers (excluding Electricians)
72	Metal, Machinery and Related Trades Workers
73	Handicraft and Printing Workers
74	Electrical and Electronic Trades Workers
75	Food Processing, Woodworking, Garment and Other Craft and Related Trades Workers

8	Plant and Machine Operators and Assemblers
81	Stationary Plant and Machine Operators
82	Assemblers
83	Drivers and Mobile Plant Operators

9	Elementary Occupations
91	Cleaners and Helpers
92	Agricultural, Forestry and Fishery Labourers
93	Labourers in Mining, Construction, Manufacturing and Transport
94	Food Preparation Assistants
95	Street and Related Sales and Services Workers
96	Refuse Workers and Other Elementary Workers

0	Armed Forces Occupations
01	Commissioned Armed Forces Officers
02	Non-commissioned Armed Forces Officers
03	Armed Forces Occupations, Other Ranks

```{r isco88_2, include = TRUE, warning=F,message=F}
# Get non-ISCO, country-specific occupation codes
socin$au_occ <- socin2$AU_OCC87
socin$it_occ <- zap_labels(socin2$IT_OCC87)
socin[which(socin$cntry == 380 & socin$year == 1992),]$it_occ <- socin2[which(socin2$V5 == 380 & socin2$V4 == 1992),]$IT_OCC92
socin$gbr_occ <- zap_labels(socin2$GB_OCC87)
socin[which(socin$cntry == 826 & socin$year == 1992),]$gbr_occ <- socin2[which(socin2$V5 == 826 & socin2$V4 == 1992),]$GB_OCC92
socin$us_occ <- zap_labels(socin2$US_OCC87)
socin$pl_occ <- zap_labels(socin2$PL_OCC87)
socin$se_occ <- zap_labels(socin2$SE_OCC92)
socin$bg_occ <- zap_labels(socin2$BG_OCC99)
socin$fr_occ <- zap_labels(socin2$FR_OCC99)
socin$jp_occ <- zap_labels(socin2$JP_OCC99)


# Australia 1987

#isco88 4-digit not available

# Data are in ASCO First Edition, emailed Kelley and Evans 10-Jun-20 to ask for correspondance tables

# Create rough isco88_2digit, taken from ZA1680_cdb.pdf pp. 184-191

socin <- socin %>%
  mutate(
    isco88_2digit_au = case_when(
      au_occ >= 1100 & au_occ <= 1199 ~ 11, 
      au_occ >= 1200 & au_occ <= 1299 ~ 14,
      au_occ >= 1300 & au_occ <= 1303 ~ 12,
      au_occ >= 1304 & au_occ <= 1399 ~ 13,
      au_occ >= 1400 & au_occ <= 1499 ~ 61,
      au_occ >= 1500 & au_occ <= 1699 ~ 14,
      au_occ >= 2000 & au_occ <= 2199 ~ 21, # Natural scientists
      au_occ >= 2200 & au_occ <= 2299 ~ 21, # Building professionals
      au_occ >= 2300 & au_occ <= 2399 ~ 22,
      au_occ >= 2400 & au_occ <= 2599 ~ 23,
      au_occ >= 2600 & au_occ <= 2699 ~ 26,
      au_occ >= 2700 & au_occ <= 2799 ~ 24,
      au_occ >= 2800 & au_occ <= 2899 ~ 26,
      au_occ >= 2900 & au_occ <= 2999 ~ 26,
      au_occ >= 3000 & au_occ <= 3101 ~ 32, #Medical
      au_occ >= 3102 & au_occ <= 3299 ~ 31, #Science/Engineering
      au_occ >= 3300 & au_occ <= 3307 ~ 31, 
      au_occ >= 3400 & au_occ <= 3499 ~ 32,
      au_occ >= 3500 & au_occ <= 3599 ~ 54,
      au_occ >= 3900 & au_occ <= 3999 ~ 34,
      au_occ >= 4000 & au_occ <= 4299 ~ 72,
      au_occ >= 4300 & au_occ <= 4399 ~ 74,
      au_occ >= 4400 & au_occ <= 4499 ~ 71,
      au_occ >= 4500 & au_occ <= 4599 ~ 73,
      au_occ >= 4600 & au_occ <= 4699 ~ 72,
      au_occ >= 4700 & au_occ <= 4799 ~ 75,
      au_occ >= 4800 & au_occ <= 4899 ~ 61,
      au_occ >= 4900 & au_occ <= 4999 ~ 75,
      au_occ >= 5000 & au_occ <= 5199 ~ 41,
      au_occ >= 5200 & au_occ <= 5299 ~ 43,
      au_occ >= 5300 & au_occ <= 5399 ~ 43,
      au_occ >= 5400 & au_occ <= 5499 ~ 44,
      au_occ >= 5500 & au_occ <= 5599 ~ 43,
      au_occ >= 5600 & au_occ <= 5699 ~ 42,
      au_occ >= 5900 & au_occ <= 5905 ~ 44,
      au_occ >= 5907 & au_occ <= 5909 ~ 42,
      au_occ >= 5910 & au_occ <= 5999 ~ 44,
      au_occ >= 6000 & au_occ <= 6399 ~ 52,
      au_occ >= 6400 & au_occ <= 6499 ~ 51,
      au_occ >= 6500 & au_occ <= 6599 ~ 52,
      au_occ >= 6600 & au_occ <= 6699 ~ 53,
      au_occ >= 7000 & au_occ <= 7299 ~ 83,
      au_occ >= 7300 & au_occ <= 7399 ~ 81,
      au_occ >= 7400 & au_occ <= 7499 ~ 82,
      au_occ >= 8000 & au_occ <= 8199 ~ 93,
      au_occ >= 8200 & au_occ <= 8299 ~ 92,
      au_occ >= 8300 & au_occ <= 8399 ~ 91,
      au_occ >= 8400 & au_occ <= 8999 ~ 93,
      TRUE ~ NA_real_
    )
  )



# Italy 1987 & 1992

# From 87 codebook and https://zacat.gesis.org/webview/index/no/ZACAT/ZACAT.c.ZACAT/ISSP.d.58/Cumulations.d.72/International-Social-Survey-Programme-Social-Inequality-I-IV-ADD-ON-ISSP-1987-1992-1999-2009.s.ZA5891/Ctry-specifi-occupation-respondent-spouse-father-mother-.h.9/Respondents-national-occupation-Italy/fVariable/ZA5891_V123

# both coding schemes are identical for Italy in 1987 & 1992 in terms of the order of values, just in 1992 the values themeselves changed to starting with 1
socin <- socin %>%
  mutate(
    isco88_2digit_it1 = case_when(
      it_occ == 11 & year == 1987 ~ 13,
      it_occ == 12 & year == 1987 ~ 12,
      it_occ == 13 & year == 1987 ~ 26,
      it_occ == 14 & year == 1987 ~ 11,
      it_occ == 21 & year == 1987 ~ 11,
      it_occ == 22 & year == 1987 ~ 23,
      it_occ == 23 & year == 1987 ~ 34,
      it_occ == 24 & year == 1987 ~ 1,
      it_occ == 25 & year == 1987 ~ 33,
      it_occ == 26 & year == 1987 ~ 41,
      it_occ == 27 & year == 1987 ~ 26,
      it_occ == 31 & year == 1987 ~ 81,
      it_occ == 32 & year == 1987 ~ 2,
      it_occ == 33 & year == 1987 ~ 91,
      it_occ == 34 & year == 1987 ~ 92,
      it_occ == 41 & year == 1987 ~ 24,
      it_occ == 42 & year == 1987 ~ 52,
      it_occ == 43 & year == 1987 ~ 71,
      it_occ == 44 & year == 1987 ~ 95,
      it_occ == 45 & year == 1987 ~ 91,
      it_occ == 46 & year == 1987 ~ 61,
      it_occ == 47 & year == 1987 ~ 91,
      TRUE ~ NA_real_
    )
  )

# 1992

socin <- socin %>%
  mutate(
    isco88_2digit_it2 = case_when(
      it_occ == 1 & year == 1992 ~ 13,
      it_occ == 2 & year == 1992 ~ 12,
      it_occ == 3 & year == 1992 ~ 26,
      it_occ == 4 & year == 1992 ~ 11,
      it_occ == 5 & year == 1992 ~ 11,
      it_occ == 6 & year == 1992 ~ 23,
      it_occ == 7 & year == 1992 ~ 34,
      it_occ == 8 & year == 1992 ~ 1,
      it_occ == 9 & year == 1992 ~ 33,
      it_occ == 10 & year == 1992 ~ 41,
      it_occ == 11 & year == 1992 ~ 26,
      it_occ == 12 & year == 1992 ~ 81,
      it_occ == 13 & year == 1992 ~ 2,
      it_occ == 14 & year == 1992 ~ 91,
      it_occ == 15 & year == 1992 ~ 92,
      it_occ == 16 & year == 1992 ~ 24,
      it_occ == 17 & year == 1992 ~ 52,
      it_occ == 18 & year == 1992 ~ 71,
      it_occ == 19 & year == 1992 ~ 95,
      it_occ == 20 & year == 1992 ~ 91,
      it_occ == 21 & year == 1992 ~ 61,
      it_occ == 22 & year == 1992 ~ 91,
      TRUE ~ NA_real_
    )
  )


# Great Britain 1987

socin <- socin %>%
  mutate(
    isco88_2digit_gbr1 = case_when(
      gbr_occ == 1 & year == 1987 ~ 11,
      gbr_occ == 2 & year == 1987 ~ 12,
      gbr_occ == 3 & year == 1987 ~ 13,
      gbr_occ == 4 & year == 1987 ~ 24,
      gbr_occ == 5 & year == 1987 ~ 14,
      gbr_occ >= 6 & gbr_occ <= 8 & year == 1987 ~ 11,
      gbr_occ == 9 & year == 1987 ~ 14,
      gbr_occ >= 10 & gbr_occ <= 18 & year == 1987 ~ 23,
      gbr_occ >= 19 & gbr_occ <= 23 & year == 1987 ~ 26,
      gbr_occ >= 24 & gbr_occ <= 33 & year == 1987 ~ 21,
      gbr_occ >= 34 & gbr_occ <= 39 & year == 1987 ~ 31,
      gbr_occ == 40 & year == 1987 ~ 61,
      gbr_occ >= 41 & gbr_occ <= 42 & year == 1987 ~ 1,
      gbr_occ == 43 & year == 1987 ~ 26,
      gbr_occ >= 44 & gbr_occ <= 45 & year == 1987 ~ 33,
      gbr_occ >= 46 & gbr_occ <= 51 & year == 1987 ~ 41,
      gbr_occ == 52 & year == 1987 ~ 33,
      gbr_occ == 54 & year == 1987 ~ 33,
      gbr_occ >= 55 & gbr_occ <= 57 & year == 1987 ~ 52,
      gbr_occ >= 58 & gbr_occ <= 59 & year == 1987 ~ 2,
      gbr_occ == 60 & year == 1987 ~ 33,
      gbr_occ >= 61 & gbr_occ <= 62 & year == 1987 ~ 54,
      gbr_occ == 63 & year == 1987 ~ 33,
      gbr_occ == 67 & year == 1987 ~ 33,
      gbr_occ == 71 & year == 1987 ~ 33,
      gbr_occ >= 64 & gbr_occ <= 66 & year == 1987 ~ 75,
      gbr_occ >= 68 & gbr_occ <= 70 & year == 1987 ~ 51,
      gbr_occ >= 72 & gbr_occ <= 75 & year == 1987 ~ 91,
      gbr_occ == 76 & year == 1987 ~ 71,
      gbr_occ == 77 & year == 1987 ~ 92,
      gbr_occ == 78 & year == 1987 ~ 92,
      gbr_occ == 79 & year == 1987 ~ 81,
      gbr_occ == 80 & year == 1987 ~ 62,
      gbr_occ == 81 & year == 1987 ~ 61,
      gbr_occ == 82 & year == 1987 ~ 92,
      gbr_occ == 83 & year == 1987 ~ 92,
      TRUE ~ NA_real_
    )
  )

# GB 1992 

# https://zacat.gesis.org/webview/index.jsp?study=http%3A%2F%2F193.175.238.79%3A80%2Fobj%2FfStudy%2FZA5891&variable=http%3A%2F%2F193.175.238.79%3A80%2Fobj%2FfVariable%2FZA5891_V123&mode=documentation&submode=variable&top=yes&language=no

socin <- socin %>%
  mutate(
    isco88_2digit_gbr2 = case_when(
      gbr_occ == 10 & year == 1992 ~ 11,
      gbr_occ == 11 & year == 1992 ~ 13,
      gbr_occ == 12 & year == 1992 ~ 13,
      gbr_occ == 13 & year == 1992 ~ 12,
      gbr_occ == 14 & year == 1992 ~ 24,
      gbr_occ == 15 & year == 1992 ~ 54,
      gbr_occ == 16 & year == 1992 ~ 12,
      gbr_occ == 17 & year == 1992 ~ 14,
      gbr_occ == 19 & year == 1992 ~ 14,
      gbr_occ == 20 & year == 1992 ~ 21,
      gbr_occ == 21 & year == 1992 ~ 21,
      gbr_occ == 22 & year == 1992 ~ 22,
      gbr_occ == 23 & year == 1992 ~ 23,
      gbr_occ == 24 & year == 1992 ~ 26,
      gbr_occ == 25 & year == 1992 ~ 24,
      gbr_occ == 26 & year == 1992 ~ 21,
      gbr_occ == 27 & year == 1992 ~ 25,
      gbr_occ == 29 & year == 1992 ~ 34,
      gbr_occ == 30 & year == 1992 ~ 31,
      gbr_occ == 31 & year == 1992 ~ 31,
      gbr_occ == 32 & year == 1992 ~ 35,
      gbr_occ == 33 & year == 1992 ~ 33,
      gbr_occ == 34 & year == 1992 ~ 32,
      gbr_occ == 35 & year == 1992 ~ 34,
      gbr_occ == 36 & year == 1992 ~ 33,
      gbr_occ == 37 & year == 1992 ~ 34,
      gbr_occ == 38 & year == 1992 ~ 34,
      gbr_occ == 39 & year == 1992 ~ 31,
      gbr_occ == 40 & year == 1992 ~ 44,
      gbr_occ == 41 & year == 1992 ~ 43,
      gbr_occ == 42 & year == 1992 ~ 43,
      gbr_occ == 43 & year == 1992 ~ 44,
      gbr_occ == 44 & year == 1992 ~ 42,
      gbr_occ == 45 & year == 1992 ~ 51,
      gbr_occ == 46 & year == 1992 ~ 51,
      gbr_occ == 49 & year == 1992 ~ 51,
      gbr_occ == 50 & year == 1992 ~ 71,
      gbr_occ == 51 & year == 1992 ~ 72,
      gbr_occ == 52 & year == 1992 ~ 74,
      gbr_occ == 53 & year == 1992 ~ 72,
      gbr_occ == 54 & year == 1992 ~ 72,
      gbr_occ == 55 & year == 1992 ~ 75,
      gbr_occ == 56 & year == 1992 ~ 75,
      gbr_occ == 57 & year == 1992 ~ 75,
      gbr_occ == 58 & year == 1992 ~ 75,
      gbr_occ == 59  & year == 1992 ~ 75,
      gbr_occ == 60  & year == 1992 ~ 1,
      gbr_occ == 61  & year == 1992 ~ 54,
      gbr_occ == 62  & year == 1992 ~ 52,
      gbr_occ == 63  & year == 1992 ~ 52,
      gbr_occ == 64  & year == 1992 ~ 14,
      gbr_occ == 65  & year == 1992 ~ 51,
      gbr_occ == 66  & year == 1992 ~ 51,
      gbr_occ == 67  & year == 1992 ~ 91,
      gbr_occ == 69  & year == 1992 ~ 54,
      gbr_occ == 70  & year == 1992 ~ 52,
      gbr_occ == 71  & year == 1992 ~ 52,
      gbr_occ == 72  & year == 1992 ~ 95,
      gbr_occ == 73  & year == 1992 ~ 95,
      gbr_occ == 79  & year == 1992 ~ 95,
      gbr_occ == 80  & year == 1992 ~ 94,
      gbr_occ == 81  & year == 1992 ~ 82,
      gbr_occ == 82  & year == 1992 ~ 81,
      gbr_occ == 83  & year == 1992 ~ 81,
      gbr_occ == 84  & year == 1992 ~ 81,
      gbr_occ == 85  & year == 1992 ~ 82,
      gbr_occ == 86  & year == 1992 ~ 82,
      gbr_occ == 87  & year == 1992 ~ 83,
      gbr_occ == 88  & year == 1992 ~ 83,
      gbr_occ == 89  & year == 1992 ~ 81,
      gbr_occ == 90  & year == 1992 ~ 92,
      gbr_occ == 91  & year == 1992 ~ 93,
      gbr_occ == 92  & year == 1992 ~ 93,
      gbr_occ == 93  & year == 1992 ~ 93,
      gbr_occ == 94  & year == 1992 ~ 95,
      gbr_occ == 95  & year == 1992 ~ 95,
      gbr_occ == 99  & year == 1992 ~ 96,
      TRUE ~ NA_real_
    )
  )


# Poland 1987

socin <- socin %>%
  mutate(
    isco88_2digit_pl = case_when(
      pl_occ == 1 & year == 1987 ~ 24, # Professionals
      pl_occ == 2 & year == 1987 ~ 12, # Managers
      pl_occ == 3 & year == 1987 ~ 33, # Semiprof. white-collar
      pl_occ == 4 & year == 1987 ~ 41, # Office workers
      pl_occ == 5 & year == 1987 ~ 52, # Service workers manual/non
      pl_occ == 6 & year == 1987 ~ 11, # Owners of manufacturing, trades, artisans
      pl_occ == 7 & year == 1987 ~ 13, # Foremen
      pl_occ == 8 & year == 1987 ~ 71, # Skilled manual
      pl_occ == 9 & year == 1987 ~ 81, # Semi-skilled
      pl_occ == 10 & year == 1987 ~ 91, # Unskilled
      pl_occ == 11 & year == 1987 ~ 61, # Farmers
      pl_occ == 12 & year == 1987 ~ 92, # Ag workers/laborers
      TRUE ~ NA_real_
    )
  )

# US 1987

# both Recoding to isco88 & isco88_2digit possible

# From US87 to USt

# Save the text for later uses
us87st <- "1=23;2=43;3=64;4=64;5=64;6=44;10=48;11=75;12=55;13=19;14=57;  15=45;20=46;21=47;22=258;23=26;24=159;25=15;26=159;30=179;31=36;32=164;33=165;34=66;  
35=68;36=67;42=77;43=74;44=77;45=45;51=75;52=75;53=49;54=76;55=56;56=27;61=89;62=85;  
63=87;64=96;65=84;71=88;72=86;73=89;74=97;75=95;76=98;80=203;81=204;82=205;83=206;84=446;  85=106;86=176;90=177;91=23;92=169;93=167;94=168;95=173;96=169;100=174;101=19;102=136;103=113; 104=114;105=115;110=116;111=127;112=128;113=133;114=118;115=135;116=119;120=123;121=125;122=124;123=137;124=138;125=139;126=143;130=144;131=149;132=145;133=147;134=148;135=117;140=154;141=159;142=156;143=155;144=157;145=158;150=223;151=224;152=217;153=189;154=56; 155=215;156=225;161=63;162=214;163=159;164=227;165=235;170=36;171=228;172=233;173=235;  174=163;175=187;180=159;181=183;182=193;183=185;184=19;185=186;190=185;191=189;192=197; 193=198; 194=169;195=19;201=5;202=7;203=28;205=19;210=7;211=18;212=19;213=35;215=166;216=16;  220=5;221=497;222=33;223=19;224=17;225=29;226=823;230=19;231=9;233=243;235=14;240=14;  245=55;260=256;261=284;262=243;264=277;265=13;266=278;270=13;271=255;280=285;281=257;282=259;  283=185;284=263;285=259;301=303;303=339;305=25;310=276;311=377;312=303;313=307;314=275; 315=359;320=303;321=234;323=303;325=303;326=24;330=329;331=307;332=307;333=357;334=366;  341=305;342=337;343=304;344=345;345=303;350=309;355=345;360=305;361=307;362=384;363=254; 364=303;370=19;371=313;372=19;374=276;375=234;376=303;381=307;382=303;384=349;385=19;390=257;391=303;392=368;394=234;395=37;401=505;402=436;403=487;404=36;405=633;410=553;411=564;412=599;413=567;415=554;416=569;420=566;421=558;422=633;423=734;424=843;425=185;426=633; 430=533;431=576;433=523; 434=737;435=649;436=558; 440=565;441=19;442=713;443=658;444=674;  445=514;446=724;450=496; 452=35;453=235;454=518;455=824;456=824;461=518;462=639;470=503;  471=216;472=19;473=503;474=506;475=525;480=517;481=503;482=503;483=518;484=538;485=523;  486=503;491=507;492=503;495=549;501=768;502=503;503=675;504=675;505=773;506=677;510=556;  511=579;512=583;514=645;515=649;516=535;520=556;521=584;522=557;523=587;525=695;530=633;  531=734;533=707;534=558;535=558;536=596;540=547;542=633;543=675;545=633;546=188;550=558;  551=633;552=503;554=503;560=553;561=633;562=635;563=633;571=503;580=430;590=431;601=558;  602=508;603=615;604=754;605=866;610=36;611=633;612=726;613=633;614=598;615=573;620=633;  621=633;622=715;623=864;624=799;625=798;626=724;630=633;631=686;633=686;634=888;635=723;  636=674;640=617;641=599;642=519;643=754;644=759;645=633;650=708;651=644;652=637;653=684;  656=599;660=717;661=829;662=633;663=633;664=745;665=784;666=633;670=749;671=739;672=738;  673=739;674=365;680=633;681=684;690=479;692=633;694=455;695=653;701=498;703=808;704=465;  705=805;706=856;710=824;711=813;712=824;713=825;714=809;715=329;740=427;750=865;751=558;  752=498;753=599;754=875;755=474;760=843;761=494;762=243;763=804;764=547;770=889;780=487;  785=407;801=473;802=475;821=477;822=479;823=479;824=477;901=448;902=448;903=448;910=434; 911=443;912=433;913=444;914=433;915=433;916=433;921=445;922=446;923=95;924=447;925=207; 926=207;931=465;932=469;933=449;934=456;935=456;940=469;941=469;942=456;943=454;944=456;945=457;950=433;952=468;953=464;954=467;960=425;961=6;962=414;963=423;964=6;965=423;980=406; 981=404;982=405;983=403;984=407"



# From Ust to isco88
# have to code as two strings then paste, otherwise string is too long for R (on Nate's CPU at least)
a <- "003=1110;004=1120;005=1120;006=1120;007=1231;008=1232;009=1233;013=1233;014=1229;015=1229;016=5121;017=1226;018=5143;019=1229;023=2411;024=3412;025=3410;026=2149;027=2412;028=3416;029=3416;033=3416;034=2419;035=3151;036=3444;037=1229;043=2141;044=2145;045=2147;046=2147;047=2146;048=2146;049=2145;053=2142;054=2213;055=2143;056=2149;057=2145;058=2145;059=2149;063=2148;064=2131;065=2121;066=2121;067=2122;068=2121;069=2111;073=2113;074=2112;075=2114;076=2110;077=2213;078=2211;079=2213;083=2221;084=2221;085=2222;086=2223;087=3224;088=3226;089=3229;095=2230;096=2224;097=3223;098=3226;099=3226;103=3226;104=3229;105=3226;106=3221;113=2310;114=2310;115=2310;116=2310;117=2310;118=2310;119=2310;123=2310;124=2310;125=2310;126=2310;127=2310;128=2310;129=2310;133=2310;134=2310;135=2310;136=2310;137=2310;138=2310;139=2310;143=2310;144=2310;145=2310;146=2310;147=2321;148=2321;149=2322;153=2310;154=2310;155=2332;156=2331;157=2321;158=2340;159=2359;163=2412;164=2432;165=2431;166=2441;167=2445;168=2442;169=2442;173=2141;174=2446;175=3460;176=2460;177=3480;178=2421;179=2422;183=2451;184=2451;185=3471;186=3473;187=2455;188=2452;189=3131;193=3473;194=3470;195=2451;197=2419;198=3472;199=3475;203=3211;204=3225;205=2432;206=3133;207=3231;208=3211;213=3113;214=3119;215=3115;216=3119;217=3118;218=3118;223=3211;224=3111;225=3111;226=3143;227=3144;228=3132;229=2132;233=3123;234=2421;235=3100;243=1314;253=3412;254=3413;255=3411;256=3429;257=3429;258=3415;259=3415;263=5220;264=5220;265=5220;266=5220;267=5220;268=5220;269=5220;274=5220;275=5220;276=4211;277=9110;278=9112;283=5210;284=3417;285=5200;303=1240;304=1240;305=1231;306=4223;307=4133;308=3122;309=3122;313=4115;314=4111;315=4111;316=4190;317=4222;318=4221;319=4222;323=4222;325=4190;326=4100;327=4132;328=4121;329=4141;335=4141;336=4190;337=4121;338=4121;339=4121;343=4121;344=4114;345=4190;346=4142;347=4114;348=4223;349=3132;353=3132;354=4142;355=4142;356=4212;357=9151;359=4133;363=4132;364=4131;365=4131;366=9153;368=4131;369=4122;373=4133;374=4132;375=3417;376=3417;377=3443;378=4215;379=4100;383=4212;384=4143;385=4113;386=4122;387=3310;389=4190;403=8264;404=5122;405=5121;406=5131;407=9132;413=5161;414=5162;415=9152;416=5161;417=5161;418=5162;423=5162;424=5163;425=8312;426=5169;427=5169;433=5121;434=5123;435=5123;436=5122;437=5122;438=5123;439=9132;443=5123;444=5120;445=3225;446=3221;447=5132;448=9141;449=9131;453=9140;454=9151;455=7143;456=5141;457=5141;458=5141;459=9152;463=5113;464=9152;465=9152;466=9151;467=3460;468=5131;469=5100;473=6133;474=6113;475=1311;476=1311;477=6132;479=9211;483=6151;484=9211;485=6132;486=9211;487=9211;488=7415;489=3152;494=6141;495=9142;496=6141;497=3142;498=6150;499=6154;503=7230;505=7231;506=7231;507=7231;508=7232;509=7230;514=7213;515=7232;516=7233;517=7233;518=7233;519=7233;523=7242;525=7242;526=7241;527=7245;529=7244;533=7241;534=7241;535=7310;536=7222;538=7242;539=7233;543=7233;544=7233;547=7230;549=7230;553=7122;554=7124;"

b <- "555=7240;556=7141;557=7136;558=7510;563=7122;564=7122;565=7132;566=7132;567=7132;569=7124;573=7129;575=7137;576=7137;577=7245;579=7141;583=7141;584=7133;585=7136;587=7136;588=7123;589=7135;593=7134;594=8332;595=7131;596=7213;597=7214;598=8113;599=7129;613=7110;614=8113;615=7112;616=8111;617=7111;633=7510;634=7222;635=7222;636=7311;637=7222;639=7223;643=7213;644=7224;645=7222;646=7222;647=7313;649=7343;653=7213;654=7213;655=7213;656=7422;657=7422;658=7422;659=7420;666=7433;667=7433;668=7437;669=7442;673=7436;674=7436;675=7310;676=7310;677=7322;678=7311;679=7345;683=8282;684=7310;686=7411;687=7412;688=8270;689=9321;693=7331;694=8163;695=8161;696=8160;699=8160;703=7223;704=8211;705=8211;706=8211;707=8122;708=8211;709=8223;713=7221;714=7223;715=8211;717=8400;719=8122;723=8223;724=8123;725=8290;726=8141;727=8141;728=8240;729=8240;729=8262;733=8141;734=8251;735=7344;736=7341;737=8251;738=8261;743=8269;744=8263;745=8266;747=8264;748=8264;749=8269;753=8229;754=8290;755=8229;756=8151;757=8154;758=8290;759=7142;763=8274;764=8275;765=8290;766=8131;768=8151;769=8290;773=3132;774=8251;777=8290;779=8290;783=7212;784=7212;785=8290;786=7520;787=7520;789=7141;793=7323;794=7224;795=7520;796=8290;797=8290;798=8290;799=8290;803=4133;804=8324;805=8322;806=8322;808=8323;809=8322;813=9152;814=9333;823=5112;824=8311;825=8312;826=8310;828=8340;829=8340;833=3141;834=8340;843=7520;844=8330;845=8333;848=8333;849=8333;853=8332;855=8332;856=8334;859=8330;863=7510;864=7234;865=9313;866=9313;867=9311;869=9313;873=9320;875=9161;876=9333;877=9333;878=9321;883=9333;885=7234;887=9142;888=9322;889=9300;905=110;909=110;739=8262"

usst88 <- paste0(a,b)
rm(a,b)
socin$us_occ <- car::recode(socin$us_occ, recodes = us87st)
socin$us_occ <- car::recode(socin$us_occ, recodes = usst88)

socin[which(socin$cntry == 840 & socin$year == 1987),]$isco88 <- socin[which(socin$cntry == 840 & socin$year == 1987),]$us_occ

# Recoding to isco88: Bulgaria 1999 (manually code to EGP6)


# Recoding to isco88: France 1999 (not found - need some French knowledge)


# Recoding to isco88: Japan 1999
socin$jp_occ <- as.numeric(socin$jp_occ)
socin$jp_occ <- car::recode(socin$jp_occ, recodes = "7 = 2265;8 = 2265;5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233; 9  = NA; 10= NA; 11 = NA")
socin[which(socin$cntry == 392 & socin$year == 1999),]$isco88 <- socin[which(socin$cntry == 392 & socin$year == 1999),]$jp_occ
jp_occ <- socin[which(socin$cntry == 392),]$isco88 
educyrsjp <- socin[which(socin$cntry == 392),]$educyrs
jp <- as.data.frame(cbind(jp_occ, educyrsjp))
jp$jp_occ <- if_else(jp$jp_occ == 4115 & jp$educyrsjp < 14, 3416, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 7233 & jp$educyrsjp > 11, 4211, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 6130 & jp$educyrsjp < 12, 9211, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 2265 & jp$educyrsjp < 16, 1229, jp$jp_occ)


socin[which(socin$cntry == 392),]$isco88 <- jp$jp_occ


# Recoding to isco88: Sweden 1992
se9288 <- "1 = 2141; 2 = 2143; 3 = 2144; 4 = 2145; 5 = 3116; 6 = 3117; 7 = 2142; 8 = 2148; 9 = 3119; 12 = 3211; 13 = 3211; 14 = 2114; 15 = 2112; 16 = 2113; 19 = 3111; 21 = 2211; 22 = 3213; 23 = 3213; 29 = 2211; 30 = 1210; 31 = 2310; 32 = 2320; 33 = 2331; 34 = 2320; 35 = 2359; 36 = 2320; 37 = 2352; 39 = 2359; 41 = 2460; 49 = 3480; 51 = 2421; 52 = 2429; 53 = 2429; 54 = 2429; 59 = 2429; 61 = 2451; 62 = 1234; 63 = 1229; 69 = 2451; 71 = 2452; 72 = 3471; 73 = 3471; 74 = 3131; 75 = 3474; 76 = 2453; 77 = 2455; 79 = 2455; 91 = 2432; 92 = 2431; 99 = 2446; 101 = 2221; 102 = 2230; 103 = 3231; 104 = 3232; 105 = 3133; 106 = 5132; 107 = 5132; 109 = 9132; 111 = 3226; 112 = 2229; 119 = 3226; 121 = 2222; 122 = 3225; 123 = 3225; 129 = 3225; 131 = 2224; 139 = 3228; 141 = 2223; 149 = 3227; 151 = 2446; 152 = 1228; 153 = 5131; 154 = 5133; 155 = 1228; 159 = 2446; 161 = 3152; 162 = 3151; 169 = 3152; 191 = 2445; 192 = 3223; 199 = 3460; 201 = 1110; 202 = 3443; 203 = 3444; 209 = 1110; 211 = 2419; 212 = 3431; 219 = 2419; 221 = 2412; 222 = 3423; 229 = 2412; 231 = 2411; 232 = 2411; 239 = 4121; 241 = 4115; 242 = 4111; 249 = 4190; 251 = 2131; 252 = 3122; 259 = 3121; 261 = 2441; 262 = 2122; 269 = 2441; 291 = 4190; 292 = 4122; 293 = 3412; 294 = 3412; 295 = 4221; 296 = 3422; 297 = 1317; 299 = 4190; 311 = 3471; 312 = 3413; 313 = 3419; 319 = 3419; 321 = 3416; 331 = 1314; 332 = 5220; 333 = 5220; 339 = 5220; 399 = 5220; 400 = 1311; 401 = 6112; 402 = 6130; 403 = 6130; 404 = 6130; 405 = 6130; 406 = 6129; 409 = 6112; 411 = 6112; 412 = 6121; 413 = 6112; 414 = 6129; 419 = 6121; 421 = 6154; 431 = 6152; 432 = 6151; 439 = 6152; 441 = 6141; 449 = 6141; 501 = 7111; 509 = 7111; 511 = 8113; 521 = 8121; 531 = 8155; 599 = 7111; 601 = 3142; 602 = 3142; 603 = 3141; 609 = 3142; 611 = 8340; 612 = 8340; 619 = 8340; 621 = 3143; 629 = 3143; 631 = 8311; 640 = 8322; 641 = 8324; 642 = 8322; 643 = 9151; 649 = 8334; 651 = 3144; 652 = 5112; 653 = 5111; 659 = 5112; 661 = 4133; 662 = 3144; 663 = 8312; 664 = 4133; 669 = 4133; 671 = 4142; 673 = 3132; 674 = 3132; 675 = 3132; 679 = 4142; 681 = 4142; 682 = 9151; 689 = 4142; 691 = 4133; 699 = 9330; 701 = 8261; 702 = 7332; 703 = 7432; 705 = 8262; 706 = 7435; 707 = 3152; 709 = 7332; 711 = 7433; 712 = 7434; 713 = 7433; 714 = 7437; 715 = 7435; 716 = 7433; 719 = 7436; 721 = 7442; 722 = 7442; 723 = 8268; 729 = 8269; 731 = 8121; 732 = 8122; 733 = 8122; 735 = 7215; 736 = 7221; 737 = 7211; 739 = 8122; 741 = 7311; 742 = 7311; 743 = 3224; 744 = 3211; 745 = 7313; 746 = 7323; 749 = 7222; 751 = 8211; 752 = 7233; 753 = 7231; 754 = 7213; 755 = 7136; 756 = 7212; 757 = 7214; 758 = 8223; 759 = 7214; 761 = 7241; 762 = 7241; 763 = 8282; 764 = 7244; 765 = 7245; 766 = 3131; 769 = 8282; 771 = 6141; 772 = 8141; 773 = 8240; 775 = 7331; 776 = 7331; 777 = 7423; 779 = 8141; 781 = 7141; 782 = 7132; 783 = 7141; 789 = 7139; 791 = 7122; 793 = 7123; 794 = 7124; 795 = 7134; 796 = 7135; 799 = 7129; 801 = 7341; 802 = 7343; 803 = 8251; 804 = 7345; 805 = 8224; 809 = 8251; 811 = 7322; 812 = 7321; 813 = 8131; 814 = 7323; 819 = 8139; 821 = 8273; 822 = 7412; 823 = 8274; 824 = 8278; 825 = 9320; 826 = 7411; 827 = 8272; 828 = 8279; 829 = 8278; 831 = 8159; 832 = 8151; 833 = 8151; 834 = 8231; 835 = 8232; 839 = 8159; 841 = 8142; 842 = 8143; 843 = 8253; 849 = 8142; 851 = 7129; 852 = 8265; 853 = 7312; 854 = 7113; 859 = 7222; 861 = 8161; 869 = 8161; 871 = 8333; 872 = 8332; 873 = 8334; 879 = 9330; 881 = 9320; 882 = 9330; 889 = 9320; 891 = 9151; 901 = 5161; 902 = 9162; 903 = 5162; 904 = 3441; 905 = 5163; 906 = 5169; 909 = 5169; 911 = 1225; 912 = 5122; 913 = 5123; 914 = 5123; 915 = 4222; 916 = 5111; 919 = 5123; 921 = 5121; 929 = 5121; 931 = 9141; 932 = 9131; 939 = 9141; 941 = 5141; 942 = 5149; 949 = 5141; 951 = 9133; 952 = 9133; 959 = 9133; 961 = 3475; 971 = 5143; 979 = 5149; 981 = 110; 989 = 110"

socin$se_occ <- car::recode(socin$se_occ, recodes = se9288)

socin[which(socin$cntry == 752 & socin$year == 1992),]$isco88 <- socin[which(socin$cntry == 752 & socin$year == 1992),]$se_occ

# Truncate isco88 values and coalesce
socin <- socin %>%
  mutate(
    isco88_2digit_else = ifelse(!is.na(isco88), trunc(isco88/100), NA),
    isco88_2digit = coalesce(isco88_2digit_au,isco88_2digit_it1,isco88_2digit_it2,
                             isco88_2digit_gbr1,isco88_2digit_gbr2,isco88_2digit_pl,
                             isco88_2digit_else)
    )

```

## Covert ISCO codes

### EGP & ISEI
### Schwander & Haeusermann's scheme (adapted)

```{r occ_conversions, include = TRUE, warning=F,message=F}
# Translating from isco88 to egp
socin$egp <- occupar::isco88toEGP(isco88 = socin$isco88, n.employees = socin$nemploy, self.employed = socin$selfemp)
# EGP6
egp6 <- '"I     Service class I" = "Service I";"II    Service class II" = "Service II"; "III.a Routine non-manual, higher grade" = "Routine"; "III.b Routine non-manual, lower grade" = "Routine"; "IV.a  Self-employed with employees" = "Self"; "IV.b  Self-employed with no employees" = "Self"; "IV.c  Self-employed Farmers etc" = "Self"; "V     Manual supervisors/Lower grade technicians" = "Skilled";"VI    Skilled workers" = "Skilled"; "VII.a Unskilled workers" = "Unskilled"; "VII.b Farm labours" = "Unskilled"'

# EGP6_2, When selfemp is not available 
egp6_2 <- '"I     Service class I" = "Service I";"II    Service class II" = "Service II"; "III.a Routine non-manual, higher grade" = "Routine"; "III.b Routine non-manual, lower grade" = "Routine"; "V     Manual supervisors/Lower grade technicians" = "Skilled";"VI    Skilled workers" = "Skilled"; "VII.a Unskilled workers" = "Unskilled"; "VII.b Farm labours" = "Unskilled"'


socin <- socin %>%
  mutate(
    egp6 = car::recode(egp, recodes = egp6)
  )

## Status using Ganzeboom, De Graaf, and Treiman 1992

socin$isei <- occupar::isco88toISEI92(isco88 = socin$isco88)

```

## Father, Mother, and Spouse

```{r f&m&sp, include = TRUE, warning=F,message=F}



## Father's occupation 

# ------- #
# Australia 1987 
socin$au_focc <- zap_labels(socin2$AU_FOC87)
socin$it_focc <- zap_labels(socin2$IT_FOC92)
socin$pl_focc <- zap_labels(socin2$PL_FOC87)
  

socin <- socin %>%
  mutate(
    fisco88_2digit_au = case_when(
      au_focc >= 1100 & au_focc <= 1199 ~ 11, 
      au_focc >= 1200 & au_focc <= 1299 ~ 14,
      au_focc >= 1300 & au_focc <= 1303 ~ 12,
      au_focc >= 1304 & au_focc <= 1399 ~ 13,
      au_focc >= 1400 & au_focc <= 1499 ~ 61,
      au_focc >= 1500 & au_focc <= 1699 ~ 14,
      au_focc >= 2000 & au_focc <= 2199 ~ 21, # Natural scientists
      au_focc >= 2200 & au_focc <= 2299 ~ 21, # Building professionals
      au_focc >= 2300 & au_focc <= 2399 ~ 22,
      au_focc >= 2400 & au_focc <= 2599 ~ 23,
      au_focc >= 2600 & au_focc <= 2699 ~ 26,
      au_focc >= 2700 & au_focc <= 2799 ~ 24,
      au_focc >= 2800 & au_focc <= 2899 ~ 26,
      au_focc >= 2900 & au_focc <= 2999 ~ 26,
      au_focc >= 3000 & au_focc <= 3101 ~ 32, #Medical
      au_focc >= 3102 & au_focc <= 3299 ~ 31, #Science/Engineering
      au_focc >= 3300 & au_focc <= 3307 ~ 31, 
      au_focc >= 3400 & au_focc <= 3499 ~ 32,
      au_focc >= 3500 & au_focc <= 3599 ~ 54,
      au_focc >= 3900 & au_focc <= 3999 ~ 34,
      au_focc >= 4000 & au_focc <= 4299 ~ 72,
      au_focc >= 4300 & au_focc <= 4399 ~ 74,
      au_focc >= 4400 & au_focc <= 4499 ~ 71,
      au_focc >= 4500 & au_focc <= 4599 ~ 73,
      au_focc >= 4600 & au_focc <= 4699 ~ 72,
      au_focc >= 4700 & au_focc <= 4799 ~ 75,
      au_focc >= 4800 & au_focc <= 4899 ~ 61,
      au_focc >= 4900 & au_focc <= 4999 ~ 75,
      au_focc >= 5000 & au_focc <= 5199 ~ 41,
      au_focc >= 5200 & au_focc <= 5299 ~ 43,
      au_focc >= 5300 & au_focc <= 5399 ~ 43,
      au_focc >= 5400 & au_focc <= 5499 ~ 44,
      au_focc >= 5500 & au_focc <= 5599 ~ 43,
      au_focc >= 5600 & au_focc <= 5699 ~ 42,
      au_focc >= 5900 & au_focc <= 5905 ~ 44,
      au_focc >= 5907 & au_focc <= 5909 ~ 42,
      au_focc >= 5910 & au_focc <= 5999 ~ 44,
      au_focc >= 6000 & au_focc <= 6399 ~ 52,
      au_focc >= 6400 & au_focc <= 6499 ~ 51,
      au_focc >= 6500 & au_focc <= 6599 ~ 52,
      au_focc >= 6600 & au_focc <= 6699 ~ 53,
      au_focc >= 7000 & au_focc <= 7299 ~ 83,
      au_focc >= 7300 & au_focc <= 7399 ~ 81,
      au_focc >= 7400 & au_focc <= 7499 ~ 82,
      au_focc >= 8000 & au_focc <= 8199 ~ 93,
      au_focc >= 8200 & au_focc <= 8299 ~ 92,
      au_focc >= 8300 & au_focc <= 8399 ~ 91,
      au_focc >= 8400 & au_focc <= 8999 ~ 93,
      TRUE ~ NA_real_
    )
  )


# Italy 1992

socin <- socin %>%
  mutate(
    fisco88_2digit_it = case_when(
      it_focc == 1 & year == 1992 ~ 13,
      it_focc == 2 & year == 1992 ~ 12,
      it_focc == 3 & year == 1992 ~ 26,
      it_focc == 4 & year == 1992 ~ 11,
      it_focc == 5 & year == 1992 ~ 11,
      it_focc == 6 & year == 1992 ~ 23,
      it_focc == 7 & year == 1992 ~ 34,
      it_focc == 8 & year == 1992 ~ 1,
      it_focc == 9 & year == 1992 ~ 33,
      it_focc == 10 & year == 1992 ~ 41,
      it_focc == 11 & year == 1992 ~ 26,
      it_focc == 12 & year == 1992 ~ 81,
      it_focc == 13 & year == 1992 ~ 2,
      it_focc == 14 & year == 1992 ~ 91,
      it_focc == 15 & year == 1992 ~ 92,
      it_focc == 16 & year == 1992 ~ 24,
      it_focc == 17 & year == 1992 ~ 52,
      it_focc == 18 & year == 1992 ~ 71,
      it_focc == 19 & year == 1992 ~ 95,
      it_focc == 20 & year == 1992 ~ 91,
      it_focc == 21 & year == 1992 ~ 61,
      it_focc == 22 & year == 1992 ~ 91,
      TRUE ~ NA_real_
    )
  )

# Poland 1987 
socin <- socin %>%
  mutate(
    fisco88_2digit_pl = case_when(
      pl_focc == 1 & year == 1987 ~ 24, # Professionals
      pl_focc == 2 & year == 1987 ~ 12, # Managers
      pl_focc == 3 & year == 1987 ~ 33, # Semiprof. white-collar
      pl_focc == 4 & year == 1987 ~ 41, # Office workers
      pl_focc == 5 & year == 1987 ~ 52, # Service workers manual/non
      pl_focc == 6 & year == 1987 ~ 11, # Owners of manufacturing, trades, artisans
      pl_focc == 7 & year == 1987 ~ 13, # Foremen
      pl_focc == 8 & year == 1987 ~ 71, # Skilled manual
      pl_focc == 9 & year == 1987 ~ 81, # Semi-skilled
      pl_focc == 10 & year == 1987 ~ 91, # Unskilled
      pl_focc == 11 & year == 1987 ~ 61, # Farmers
      pl_focc == 12 & year == 1987 ~ 92, # Ag workers/laborers
      TRUE ~ NA_real_
    )
  )



# Philippines 1992 (not found)
# Slovenia 1992 (not found)
# France 1999 (not found)
# Philippines 1999 (not found)
# Ireland 1999 (not found)
# ------- #
socin <- socin %>%
  mutate(
    fisco88 = v70,
    f_jtype = v71
  )

# Us 1987 
socin$us_foc <- zap_labels(socin2$US_FOC87)
socin$us_foc <- car::recode(socin$us_foc, recodes = us87st)
socin$us_foc <- car::recode(socin$us_foc, recodes = usst88)

socin[which(socin$cntry == 840 & socin$year == 1987),]$fisco88 <- socin[which(socin$cntry == 840 & socin$year == 1987),]$us_foc

# Sweden 1992
socin$se_foc <- zap_labels(socin2$SE_FOC92)
socin$se_foc <- car::recode(socin$se_foc, recodes = se9288)

socin[which(socin$cntry == 752 & socin$year == 1992),]$fisco88 <- socin[which(socin$cntry == 752 & socin$year == 1992),]$se_foc


# Japan 1999 (can't code without father's education years)



# Truncate and coalesce 

socin <- socin %>%
  mutate(
    fisco88_2digit_else = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
    fisco88_2digit = coalesce(fisco88_2digit_au,fisco88_2digit_it,fisco88_2digit_pl,
                             fisco88_2digit_else)
    )



## Mother's occupation 

# Israel 1999

# Slovenia 1992

socin$misco88 <- socin$v72
socin$misco88_2digit <- ifelse(!is.na(socin$misco88), trunc(socin$misco88/100), NA)



## Spouse's occupation

socin$au_socc <- zap_labels(socin2$AU_SOC87)
socin$it_socc <- zap_labels(socin2$IT_SOC87)
socin[which(socin$cntry == 380 & socin$year == 1992),]$it_socc <- socin2[which(socin2$V5 == 380 & socin2$V4 == 1992),]$IT_SOC92
socin$gbr_socc <- zap_labels(socin2$GB_SOC87)
socin[which(socin$cntry == 826 & socin$year == 1992),]$gbr_socc <- socin2[which(socin2$V5 == 826 & socin2$V4 == 1992),]$GB_SOC92
socin$us_socc <- zap_labels(socin2$US_SOC87)
socin$se_socc <- zap_labels(socin2$SE_SOC92)
socin$jp_socc <- zap_labels(socin2$JP_SOC99)
socin$ph_socc <- zap_labels(socin2$PH_SOC92)

# Australia 1987 

socin <- socin %>%
  mutate(
    spisco88_2digit_au = case_when(
      au_socc >= 1100 & au_socc <= 1199 ~ 11, 
      au_socc >= 1200 & au_socc <= 1299 ~ 14,
      au_socc >= 1300 & au_socc <= 1303 ~ 12,
      au_socc >= 1304 & au_socc <= 1399 ~ 13,
      au_socc >= 1400 & au_socc <= 1499 ~ 61,
      au_socc >= 1500 & au_socc <= 1699 ~ 14,
      au_socc >= 2000 & au_socc <= 2199 ~ 21, # Natural scientists
      au_socc >= 2200 & au_socc <= 2299 ~ 21, # Building professionals
      au_socc >= 2300 & au_socc <= 2399 ~ 22,
      au_socc >= 2400 & au_socc <= 2599 ~ 23,
      au_socc >= 2600 & au_socc <= 2699 ~ 26,
      au_socc >= 2700 & au_socc <= 2799 ~ 24,
      au_socc >= 2800 & au_socc <= 2899 ~ 26,
      au_socc >= 2900 & au_socc <= 2999 ~ 26,
      au_socc >= 3000 & au_socc <= 3101 ~ 32, #Medical
      au_socc >= 3102 & au_socc <= 3299 ~ 31, #Science/Engineering
      au_socc >= 3300 & au_socc <= 3307 ~ 31, 
      au_socc >= 3400 & au_socc <= 3499 ~ 32,
      au_socc >= 3500 & au_socc <= 3599 ~ 54,
      au_socc >= 3900 & au_socc <= 3999 ~ 34,
      au_socc >= 4000 & au_socc <= 4299 ~ 72,
      au_socc >= 4300 & au_socc <= 4399 ~ 74,
      au_socc >= 4400 & au_socc <= 4499 ~ 71,
      au_socc >= 4500 & au_socc <= 4599 ~ 73,
      au_socc >= 4600 & au_socc <= 4699 ~ 72,
      au_socc >= 4700 & au_socc <= 4799 ~ 75,
      au_socc >= 4800 & au_socc <= 4899 ~ 61,
      au_socc >= 4900 & au_socc <= 4999 ~ 75,
      au_socc >= 5000 & au_socc <= 5199 ~ 41,
      au_socc >= 5200 & au_socc <= 5299 ~ 43,
      au_socc >= 5300 & au_socc <= 5399 ~ 43,
      au_socc >= 5400 & au_socc <= 5499 ~ 44,
      au_socc >= 5500 & au_socc <= 5599 ~ 43,
      au_socc >= 5600 & au_socc <= 5699 ~ 42,
      au_socc >= 5900 & au_socc <= 5905 ~ 44,
      au_socc >= 5907 & au_socc <= 5909 ~ 42,
      au_socc >= 5910 & au_socc <= 5999 ~ 44,
      au_socc >= 6000 & au_socc <= 6399 ~ 52,
      au_socc >= 6400 & au_socc <= 6499 ~ 51,
      au_socc >= 6500 & au_socc <= 6599 ~ 52,
      au_socc >= 6600 & au_socc <= 6699 ~ 53,
      au_socc >= 7000 & au_socc <= 7299 ~ 83,
      au_socc >= 7300 & au_socc <= 7399 ~ 81,
      au_socc >= 7400 & au_socc <= 7499 ~ 82,
      au_socc >= 8000 & au_socc <= 8199 ~ 93,
      au_socc >= 8200 & au_socc <= 8299 ~ 92,
      au_socc >= 8300 & au_socc <= 8399 ~ 91,
      au_socc >= 8400 & au_socc <= 8999 ~ 93,
      TRUE ~ NA_real_
    )
  )

# Italy 1987

socin <- socin %>%
  mutate(
    spisco88_2digit_it1 = case_when(
      it_socc == 11 & year == 1987 ~ 13,
      it_socc == 12 & year == 1987 ~ 12,
      it_socc == 13 & year == 1987 ~ 26,
      it_socc == 14 & year == 1987 ~ 11,
      it_socc == 21 & year == 1987 ~ 11,
      it_socc == 22 & year == 1987 ~ 23,
      it_socc == 23 & year == 1987 ~ 34,
      it_socc == 24 & year == 1987 ~ 1,
      it_socc == 25 & year == 1987 ~ 33,
      it_socc == 26 & year == 1987 ~ 41,
      it_socc == 27 & year == 1987 ~ 26,
      it_socc == 31 & year == 1987 ~ 81,
      it_socc == 32 & year == 1987 ~ 2,
      it_socc == 33 & year == 1987 ~ 91,
      it_socc == 34 & year == 1987 ~ 92,
      it_socc == 41 & year == 1987 ~ 24,
      it_socc == 42 & year == 1987 ~ 52,
      it_socc == 43 & year == 1987 ~ 71,
      it_socc == 44 & year == 1987 ~ 95,
      it_socc == 45 & year == 1987 ~ 91,
      it_socc == 46 & year == 1987 ~ 61,
      it_socc == 47 & year == 1987 ~ 91,
      TRUE ~ NA_real_
    )
  )

# Italy 1992

socin <- socin %>%
  mutate(
    spisco88_2digit_it2 = case_when(
      it_socc == 1 & year == 1992 ~ 13,
      it_socc == 2 & year == 1992 ~ 12,
      it_socc == 3 & year == 1992 ~ 26,
      it_socc == 4 & year == 1992 ~ 11,
      it_socc == 5 & year == 1992 ~ 11,
      it_socc == 6 & year == 1992 ~ 23,
      it_socc == 7 & year == 1992 ~ 34,
      it_socc == 8 & year == 1992 ~ 1,
      it_socc == 9 & year == 1992 ~ 33,
      it_socc == 10 & year == 1992 ~ 41,
      it_socc == 11 & year == 1992 ~ 26,
      it_socc == 12 & year == 1992 ~ 81,
      it_socc == 13 & year == 1992 ~ 2,
      it_socc == 14 & year == 1992 ~ 91,
      it_socc == 15 & year == 1992 ~ 92,
      it_socc == 16 & year == 1992 ~ 24,
      it_socc == 17 & year == 1992 ~ 52,
      it_socc == 18 & year == 1992 ~ 71,
      it_socc == 19 & year == 1992 ~ 95,
      it_socc == 20 & year == 1992 ~ 91,
      it_socc == 21 & year == 1992 ~ 61,
      it_socc == 22 & year == 1992 ~ 91,
      TRUE ~ NA_real_
    )
  )


# Great Britain 1987

socin <- socin %>%
  mutate(
    spisco88_2digit_gbr1 = case_when(
      gbr_socc == 1 & year == 1987 ~ 11,
      gbr_socc == 2 & year == 1987 ~ 12,
      gbr_socc == 3 & year == 1987 ~ 13,
      gbr_socc == 4 & year == 1987 ~ 24,
      gbr_socc == 5 & year == 1987 ~ 14,
      gbr_socc >= 6 & gbr_socc <= 8 & year == 1987 ~ 11,
      gbr_socc == 9 & year == 1987 ~ 14,
      gbr_socc >= 10 & gbr_socc <= 18 & year == 1987 ~ 23,
      gbr_socc >= 19 & gbr_socc <= 23 & year == 1987 ~ 26,
      gbr_socc >= 24 & gbr_socc <= 33 & year == 1987 ~ 21,
      gbr_socc >= 34 & gbr_socc <= 39 & year == 1987 ~ 31,
      gbr_socc == 40 & year == 1987 ~ 61,
      gbr_socc >= 41 & gbr_socc <= 42 & year == 1987 ~ 1,
      gbr_socc == 43 & year == 1987 ~ 26,
      gbr_socc >= 44 & gbr_socc <= 45 & year == 1987 ~ 33,
      gbr_socc >= 46 & gbr_socc <= 51 & year == 1987 ~ 41,
      gbr_socc == 52 & year == 1987 ~ 33,
      gbr_socc == 54 & year == 1987 ~ 33,
      gbr_socc >= 55 & gbr_socc <= 57 & year == 1987 ~ 52,
      gbr_socc >= 58 & gbr_socc <= 59 & year == 1987 ~ 2,
      gbr_socc == 60 & year == 1987 ~ 33,
      gbr_socc >= 61 & gbr_socc <= 62 & year == 1987 ~ 54,
      gbr_socc == 63 & year == 1987 ~ 33,
      gbr_socc == 67 & year == 1987 ~ 33,
      gbr_socc == 71 & year == 1987 ~ 33,
      gbr_socc >= 64 & gbr_socc <= 66 & year == 1987 ~ 75,
      gbr_socc >= 68 & gbr_socc <= 70 & year == 1987 ~ 51,
      gbr_socc >= 72 & gbr_socc <= 75 & year == 1987 ~ 91,
      gbr_socc == 76 & year == 1987 ~ 71,
      gbr_socc == 77 & year == 1987 ~ 92,
      gbr_socc == 78 & year == 1987 ~ 92,
      gbr_socc == 79 & year == 1987 ~ 81,
      gbr_socc == 80 & year == 1987 ~ 62,
      gbr_socc == 81 & year == 1987 ~ 61,
      gbr_socc == 82 & year == 1987 ~ 92,
      gbr_socc == 83 & year == 1987 ~ 92,
      TRUE ~ NA_real_
    )
  )

# GB 1992 

# https://zacat.gesis.org/webview/index.jsp?study=http%3A%2F%2F193.175.238.79%3A80%2Fobj%2FfStudy%2FZA5891&variable=http%3A%2F%2F193.175.238.79%3A80%2Fobj%2FfVariable%2FZA5891_V123&mode=documentation&submode=variable&top=yes&language=no

socin <- socin %>%
  mutate(
    spisco88_2digit_gbr2 = case_when(
      gbr_socc == 10 & year == 1992 ~ 11,
      gbr_socc == 11 & year == 1992 ~ 13,
      gbr_socc == 12 & year == 1992 ~ 13,
      gbr_socc == 13 & year == 1992 ~ 12,
      gbr_socc == 14 & year == 1992 ~ 24,
      gbr_socc == 15 & year == 1992 ~ 54,
      gbr_socc == 16 & year == 1992 ~ 12,
      gbr_socc == 17 & year == 1992 ~ 14,
      gbr_socc == 19 & year == 1992 ~ 14,
      gbr_socc == 20 & year == 1992 ~ 21,
      gbr_socc == 21 & year == 1992 ~ 21,
      gbr_socc == 22 & year == 1992 ~ 22,
      gbr_socc == 23 & year == 1992 ~ 23,
      gbr_socc == 24 & year == 1992 ~ 26,
      gbr_socc == 25 & year == 1992 ~ 24,
      gbr_socc == 26 & year == 1992 ~ 21,
      gbr_socc == 27 & year == 1992 ~ 25,
      gbr_socc == 29 & year == 1992 ~ 34,
      gbr_socc == 30 & year == 1992 ~ 31,
      gbr_socc == 31 & year == 1992 ~ 31,
      gbr_socc == 32 & year == 1992 ~ 35,
      gbr_socc == 33 & year == 1992 ~ 33,
      gbr_socc == 34 & year == 1992 ~ 32,
      gbr_socc == 35 & year == 1992 ~ 34,
      gbr_socc == 36 & year == 1992 ~ 33,
      gbr_socc == 37 & year == 1992 ~ 34,
      gbr_socc == 38 & year == 1992 ~ 34,
      gbr_socc == 39 & year == 1992 ~ 31,
      gbr_socc == 40 & year == 1992 ~ 44,
      gbr_socc == 41 & year == 1992 ~ 43,
      gbr_socc == 42 & year == 1992 ~ 43,
      gbr_socc == 43 & year == 1992 ~ 44,
      gbr_socc == 44 & year == 1992 ~ 42,
      gbr_socc == 45 & year == 1992 ~ 51,
      gbr_socc == 46 & year == 1992 ~ 51,
      gbr_socc == 49 & year == 1992 ~ 51,
      gbr_socc == 50 & year == 1992 ~ 71,
      gbr_socc == 51 & year == 1992 ~ 72,
      gbr_socc == 52 & year == 1992 ~ 74,
      gbr_socc == 53 & year == 1992 ~ 72,
      gbr_socc == 54 & year == 1992 ~ 72,
      gbr_socc == 55 & year == 1992 ~ 75,
      gbr_socc == 56 & year == 1992 ~ 75,
      gbr_socc == 57 & year == 1992 ~ 75,
      gbr_socc == 58 & year == 1992 ~ 75,
      gbr_socc == 59  & year == 1992 ~ 75,
      gbr_socc == 60  & year == 1992 ~ 1,
      gbr_socc == 61  & year == 1992 ~ 54,
      gbr_socc == 62  & year == 1992 ~ 52,
      gbr_socc == 63  & year == 1992 ~ 52,
      gbr_socc == 64  & year == 1992 ~ 14,
      gbr_socc == 65  & year == 1992 ~ 51,
      gbr_socc == 66  & year == 1992 ~ 51,
      gbr_socc == 67  & year == 1992 ~ 91,
      gbr_socc == 69  & year == 1992 ~ 54,
      gbr_socc == 70  & year == 1992 ~ 52,
      gbr_socc == 71  & year == 1992 ~ 52,
      gbr_socc == 72  & year == 1992 ~ 95,
      gbr_socc == 73  & year == 1992 ~ 95,
      gbr_socc == 79  & year == 1992 ~ 95,
      gbr_socc == 80  & year == 1992 ~ 94,
      gbr_socc == 81  & year == 1992 ~ 82,
      gbr_socc == 82  & year == 1992 ~ 81,
      gbr_socc == 83  & year == 1992 ~ 81,
      gbr_socc == 84  & year == 1992 ~ 81,
      gbr_socc == 85  & year == 1992 ~ 82,
      gbr_socc == 86  & year == 1992 ~ 82,
      gbr_socc == 87  & year == 1992 ~ 83,
      gbr_socc == 88  & year == 1992 ~ 83,
      gbr_socc == 89  & year == 1992 ~ 81,
      gbr_socc == 90  & year == 1992 ~ 92,
      gbr_socc == 91  & year == 1992 ~ 93,
      gbr_socc == 92  & year == 1992 ~ 93,
      gbr_socc == 93  & year == 1992 ~ 93,
      gbr_socc == 94  & year == 1992 ~ 95,
      gbr_socc == 95  & year == 1992 ~ 95,
      gbr_socc == 99  & year == 1992 ~ 96,
      TRUE ~ NA_real_
    )
  )

# US 1987

socin$us_socc <- car::recode(socin$us_socc, recodes = us87st)
socin$us_socc <- car::recode(socin$us_socc, recodes = usst88)

socin[which(socin$cntry == 840 & socin$year == 1987),]$spisco88 <- socin[which(socin$cntry == 840 & socin$year == 1987),]$us_socc

# Sweden 1992
socin$se_socc <- car::recode(socin$se_socc, recodes = se9288)

socin[which(socin$cntry == 752 & socin$year == 1992),]$spisco88 <- socin[which(socin$cntry == 752 & socin$year == 1992),]$se_socc


# Japan 1999
socin$jp_socc <- as.numeric(socin$jp_socc)
socin$jp_socc <- car::recode(socin$jp_socc, recodes = "7 = 2265;8 = 2265;5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233; 9  = NA; 10= NA; 11 = NA")
socin[which(socin$cntry == 392 & socin$year == 1999),]$spisco88 <- socin[which(socin$cntry == 392 & socin$year == 1999),]$jp_socc
jp_socc <- socin[which(socin$cntry == 392),]$spisco88 
speducyrjp <- socin[which(socin$cntry == 392),]$speducyr
jp <- as.data.frame(cbind(jp_socc, speducyrjp))
jp$jp_socc <- if_else(jp$jp_socc == 4115 & jp$speducyrjp < 14, 3416, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 7233 & jp$speducyrjp > 11, 4211, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 6130 & jp$speducyrjp < 12, 9211, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 2265 & jp$speducyrjp < 16, 1229, jp$jp_socc)

socin[which(socin$cntry == 392),]$spisco88 <- jp$jp_socc


# Philippines 1992 (to be coded)

# Truncate and coalesce

socin <- socin %>%
  mutate(
    spisco88_2digit_else = ifelse(!is.na(spisco88), trunc(fisco88/100), NA),
    spisco88_2digit = coalesce(spisco88_2digit_au,spisco88_2digit_it1,spisco88_2digit_it2,
                             spisco88_2digit_gbr1,spisco88_2digit_gbr2,spisco88_2digit_else)
    )
## FIsCO88/MISCO88 to EGP/EGP6 and ISEI 

socin <- socin %>%
  mutate(
    f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = v68),
    f_egp6 = car::recode(f_egp, recodes = egp6),
    f_isei = occupar::isco88toISEI92(isco88 = fisco88),
    m_egp = occupar::isco88toEGP(misco88, n.employees = NULL, self.employed = NULL),
    m_egp6 = car::recode(m_egp, recodes = egp6_2),
    m_isei = occupar::isco88toISEI92(isco88 = misco88),
  )



# Select relevant variables

socin <- dplyr::select(socin, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)

```



## Add missing countries and merge



```{r m&m, include = TRUE, warning=F,message=F}
## Add missing countries
# Netherlands 1987

# ntlab <- lapply(nl87, attr, "label")


# HUNG: recode occupation. do not run until this is done. 
# NATE: We should probably ignore for now as the occupation just doesn't match properly...

# nl87 <- nl87 %>%
#   mutate(
#     cntry = 528,
#     year = 1987,
#     wave = 1987,
#     incdiff = v49,
#     age = v82,
#     ageC = ifelse(age > 75, 75, age),
#     age = case_when(                 # trim at 75     
#        age %in% c(16:24) ~ 1,        # Changed to 7 categories
#        age %in% c(25:34) ~ 2,
#        age %in% c(35:44) ~ 3,
#        age %in% c(45:54) ~ 4,
#        age %in% c(55:64) ~ 5,
#        age %in% c(65:74) ~ 6,
#        age >= 75 ~ 7,
#        TRUE ~ NA_real_
#      ),
#     sex = v83,
#     female = ifelse(sex == 9, NA, sex - 1),
#     educyrs = v87,
#     educyrs = case_when(   
#        educyrs > 22 & educyrs < 95 ~ 23, 
#        educyrs == 95 ~ 8, # still in school
#        educyrs == 96 ~ 13,
#        educyrs %in% c(97:99) ~ NA_real_,
#        TRUE ~ as.numeric(educyrs)
#     ),
#     child = NA_real_,  # not available
#     marital = v85,
#     married = case_when( 
#        marital %in% c(1:2) ~ 1, # widowed = married
#        marital %in% c(3:5) ~ 0, # divorced, separated = not married
#        TRUE ~ NA_real_
#     ),
#     union = v81,
#     union = case_when(
#       union == 2 ~ 0,
#       union == 1 ~ 1,
#       TRUE ~ NA_real_
#     ),
#     sparent = NA_real_, # not available
#     rincZ = NA_real_, # all NAs
#     income = v92,
#     hincZ = ntile(income, 10), # deciles
#     wrkst = NA_real_, # not available
#     wrkhrs = v73,
#     wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
#     egp = case_when(
#       v71 == 1 ~ 1, # Service I
#       v71 == 2 ~ 2, # Service II
#       v71 == 3 ~ 4, # Routine non-manual, lower
#       v71 == 4 ~ 3, # Routine non-manual, higher
#       v71 == 5 ~ 4, 
#       v71 == 6 ~ 
# ##### These do not map ideally, check this in the future...
#         # v71 Labels:
# #  value                 label
# #      0                   nav
# #      1 PROFESSIONAL & TECHN.
# #      2  HIGHER ADMINISTRATOR
# #      3  CLERICAL <SECRETARY>
# #      4    SALES <...MANAGER>
# #      5  SERVICE <RESTAURANT>
# #      6        SKILLED WORKER
# #      7   SEMI-SKILLED WORKER
# #      8      UNSKILLED WORKER
# #      9        FARM  <FARMER>
# #     10       NEVER HAD A JOB
# #     11              I: OTHER
# #     98             DONT KNOW
# #     99                    na
#     )
#       self.employed = v72),
#     egp6 = car::recode(egp, recodes = egp6),
#     isei = occupar::isco88toISEI92(isco88),
#     isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA), # Truncate isco88 values
#     fisco88 = v67,
#     fisco88 = case_when( # same as above
# 
#     ),
#     fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
#     f_selfemp = v68,
#     f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = f_selfemp), # nemploy missing
#     f_egp6 = car::recode(f_egp,recodes = egp6),
#     f_isei = occupar::isco88toISEI92(fisco88),
#     misco88 = NA_real_,# No mother's occupation information available for Denmark
#     misco88_2digit = NA_real_,
#     m_egp = NA_real_,
#     m_egp6 = NA_real_,
#     m_isei = NA_real_,
#     spisco88_2digit = NA_real_ # 100% missing values
#   )
# 
# 
#   
# 
# nl87 <- dplyr::select(nl87, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)

# Ireland 1987

# ielab1 <- lapply(ie87, attr, "label")
# HUNG: recode occupation. Do not run until this is done.

# ie87 <- ie87 %>%
#   mutate(
#     cntry = 372,
#     year = 1989,
#     wave = 1987,
#     incdiff = v49,
#     age = v82,
#     ageC = ifelse(age > 75, 75, age),
#     age = case_when(                 # trim at 75     
#        age %in% c(16:24) ~ 1,        # Changed to 7 categories
#        age %in% c(25:34) ~ 2,
#        age %in% c(35:44) ~ 3,
#        age %in% c(45:54) ~ 4,
#        age %in% c(55:64) ~ 5,
#        age %in% c(65:74) ~ 6,
#        age >= 75 ~ 7,
#        TRUE ~ NA_real_
#      ),
#     sex = v83,
#     female = ifelse(sex == 9, NA, sex - 1),
#     educyrs = v87,
#     educyrs = case_when(   
#        educyrs > 22 & educyrs < 95 ~ 23, 
#        educyrs == 95 ~ 8, # still in school
#        educyrs == 96 ~ 13,
#        educyrs %in% c(97:99) ~ NA_real_,
#        TRUE ~ as.numeric(educyrs)
#     ),
#     child = NA_real_,  # not available
#     marital = v85,
#     married = case_when( 
#        marital %in% c(1:2) ~ 1, # widowed = married
#        marital %in% c(3:5) ~ 0, # divorced, separated = not married
#        TRUE ~ NA_real_
#     ),
#     union = v81,
#     union = case_when(
#       union == 2 ~ 0,
#       union == 1 ~ 1,
#       TRUE ~ NA_real_
#     ),
#     sparent = NA_real_, # not available
#     rincZ = NA_real_, # all NAs
#     income = v92,
#     hincZ = ntile(income, 10), # deciles
#     wrkst = NA_real_, # not available
#     wrkhrs = v73,
#     wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
#     isco88 = v71,
#     isco88 = case_when(  # need recoding
#       
#     ),
#     egp = occupar::isco88toEGP(isco88, n.employees = NULL, self.employed = v72),
#     egp6 = car::recode(egp, recodes = egp6),
#     isei = occupar::isco88toISEI92(isco88),
#     isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA), # Truncate isco88 values
#     fisco88 = v67,
#     fisco88 = case_when(
#       
#     ),
#     fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
#     f_selfemp = v68,
#     #f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = f_selfemp), # nemploy missing
#     #f_egp6 = car::recode(f_egp,recodes = egp6),
#     #f_isei = occupar::isco88toISEI92(fisco88),
#     misco88 = NA_real_,# No mother's occupation information available for Denmark 
#     misco88_2digit = NA_real_,
#     m_egp = NA_real_,
#     m_egp6 = NA_real_, 
#     m_isei = NA_real_,
#     spisco88 = v102,
#     spisco88 = case_when( 
#       
#     ),
#     spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)
#   )
# 
# 
# 
# ie87 <- dplyr::select(ie87, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)
# 


# Denmark 1999

# dklab <- lapply(dk99, attr, "label")
# View(dklab)

dk99 <- dk99 %>%
  mutate(
    cntry = 208,
    year = 2000,
    wave = 1999,
    incdiff = v57,
    inclarge = v56,
    ageC = ifelse(age > 75, 75, age),
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,        # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    female = ifelse(sex == 9, NA, sex - 1),
    educyrs = case_when(   
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8, # still in school
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
      hhcycle %in% c(2,3,4,6,7,8,10,12,14,30) ~ 1,
      hhcycle %in% c(1,5,9,11,13,29,95) ~ 0,
      TRUE ~ NA_real_ 
    ), 
    married = case_when( 
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
    ),
    union = case_when(
      union == 2 ~ 0,
      union == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      hhcycle %in% c(2,3,4) ~ 1,
      hhcycle %in% c(1,5:95) ~ 0,
      TRUE ~ NA_real_
    ),
    rincZ = ntile(rincome, 10), # deciles
    hincZ = ntile(income, 10),
    rincO = rincome,
    wrkst = ifelse(wrkst == 4, 8, wrkst),
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    egp = occupar::isco88toEGP(isco88, n.employees = nemploy, self.employed = selfemp),
    egp6 = car::recode(egp, recodes = egp6),
    isei = occupar::isco88toISEI92(isco88),
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA), # Truncate isco88 values
    fisco88 = v142,
    fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
    f_selfemp = case_when(
      v501 == 0 ~ 0,
      v501 == 3 ~ 1,
      v501 %in% c(1,2) ~ 2,
      TRUE ~ NA_real_
    ),
    f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = f_selfemp), # nemploy missing
    f_egp6 = car::recode(f_egp,recodes = egp6),
    f_isei = occupar::isco88toISEI92(fisco88),
    misco88 = NA_real_,# No mother's occupation information available for Denmark 
    misco88_2digit = NA_real_,
    m_egp = NA_real_,
    m_egp6 = NA_real_, 
    m_isei = NA_real_,
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)
  )  


  

dk99 <- dplyr::select(dk99, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit,spisco88_2digit)

# Ireland 1999

# ielab <- lapply(ie99, attr, "label") 
# View(ielab)

ie99 <- ie99 %>%
  mutate(
    cntry = 372,
    year = 2001,
    wave = 1999,
    incdiff = v35,
    inclarge = v34,
    ageC = ifelse(age > 75, 75, age),
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,        # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    female = ifelse(sex == 9, NA, sex - 1),
    educyrs = case_when(   
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8,
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
      hhcycle %in% c(2,3,4,6,7,8,10,12,14,16,18,20,22,24) ~ 1,
      hhcycle %in% c(1,5,9,11,13,15,17,19,21,23,25) ~ 0,
      TRUE ~ NA_real_ 
    ), 
    married = case_when( 
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
    ),
    union = case_when(
      union == 2 ~ 0,
      union == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      hhcycle %in% c(2,3,4) ~ 1, 
      hhcycle %in% c(1,5:95) ~ 0,
      TRUE ~ NA_real_
    ),
    rincZ = ntile(rincome, 10),
    hincZ = ntile(income, 10),
    rincO = rincome,
    wrkst = ifelse(wrkst == 4, 8, wrkst),
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    egp = occupar::isco88toEGP(isco88, n.employees = nemploy, self.employed = selfemp),
    egp6 = car::recode(egp, recodes = egp6),
    isei = occupar::isco88toISEI92(isco88),
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA), # Truncate isco88 values
    fisco88 = v62,
    fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
    f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = NULL), # nemploy and selfemp missing (labels unkown) - some might be incorrectly coded.
    f_egp6 = car::recode(f_egp,recodes = egp6_2),
    f_isei = occupar::isco88toISEI92(fisco88),
    misco88 = NA_real_,
    misco88_2digit = NA_real_,
    m_egp = NA_real_,
    m_egp6 = NA_real_, 
    m_isei = NA_real_,
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)
  )


ie99 <- dplyr::select(ie99, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)

# Netherlands 
# nelab <- lapply(nl09, attr, "label") 

colnames(nl09) <- tolower(colnames(nl09))
nl09 <- nl09 %>%
  mutate(
    cntry = 528,
    year = 2013,
    wave = 2009,
    incdiff = v33,
    inclarge = v32,
    ageC = ifelse(age > 75, 75, age),
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,        # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    female = ifelse(sex == 9, NA, sex - 1),
    educyrs = case_when(   
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8,
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
      hhcycle %in% c(2,3,4,6,7,8,10,12,14,16,18,20,22,24,26,28) ~ 1,
      hhcycle %in% c(1,5,9,11,13,15,17,19,21,23,25,27,95) ~ 0,
      TRUE ~ NA_real_ 
    ), 
    married = case_when( 
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
    ),
    union = case_when(
      union %in% c(2,3) ~ 0,
      union == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      hhcycle %in% c(2,3,4) ~ 1, 
      hhcycle %in% c(1,5:95) ~ 0,
      TRUE ~ NA_real_
    ),
    selfemp = case_when(
      emprel %in% c(2,3,4) ~ 1,
      emprel == 1 ~ 2,
      TRUE ~ NA_real_
    ),
    rincZ = ntile(nl_rinc, 10),
    hincZ = ntile(nl_inc, 10),
    rincO = nl_rinc,
    wrkst = ifelse(wrkst == 4, 8, wrkst),
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    egp = occupar::isco88toEGP(isco88, n.employees = nemploy, self.employed = selfemp),
    egp6 = car::recode(egp, recodes = egp6),
    isei = occupar::isco88toISEI92(isco88),
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA), # Truncate isco88 values
    fisco88 = v57,
    fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
    f_egp = occupar::isco88toEGP(fisco88, n.employees = NULL, self.employed = NULL), # nemploy and selfemp missing (labels unkown) - some might be incorrectly coded.
    f_egp6 = car::recode(f_egp,recodes = egp6_2),
    f_isei = occupar::isco88toISEI92(fisco88),
    misco88 = v60,
    misco88_2digit = ifelse(!is.na(misco88), trunc(misco88/100), NA),
    m_egp = occupar::isco88toEGP(misco88, n.employees = NULL, self.employed = NULL), # nemploy and selfemp missing (labels unkown) - some might be incorrectly coded.
    m_egp6 = car::recode(m_egp,recodes = egp6_2),
    m_isei = occupar::isco88toISEI92(misco88),
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)
  )

nl09 <- dplyr::select(nl09, cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)
```

### ISSP 2019

```{r issp2019, include = TRUE, warning=F}
# ISSP 2019
colnames(socin3) <- tolower(colnames(socin3))
socin3 <- socin3 %>% 
  mutate(
    incdiff = v22,
    inclarge = v21,
    cntry = country,
    year = dateyr,
    wave = 2019,
    female = ifelse(sex == -9, NA_real_, sex - 1), # female = 1
    age = zap_labels(age),
    ageC = case_when(age >= 75 ~ 75, age == -9 ~ NA_real_, TRUE ~ age), # also a continuous measure
    age = case_when(                 # trim at 75     
       ageC %in% c(16:24) ~ 1,        # Changed to 7 categories
       ageC %in% c(25:34) ~ 2,
       ageC %in% c(35:44) ~ 3,
       ageC %in% c(45:54) ~ 4,
       ageC %in% c(55:64) ~ 5,
       ageC %in% c(65:74) ~ 6,
       ageC >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    married = case_when( # married = 1. Note: using if_else will confound NA with not married (0), make sure life partners are coded as married
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:6) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
     ),
    educyrs = case_when(                 # years in school, trim at 23 years
       educyrs > 22 & educyrs < 95 ~ 23, # 23 = 23+ years in school
       educyrs == 95 ~ 8, # still in school
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(as.character(educyrs))
     ),
     #household income and personal earnings are not comparable: sometimes monthly, sometimes yearly, 
     #in different national currency and not adjusted for inflation
    child = case_when(
       hhchildr %in% c(1:9) ~ 1,
       hhchildr %in% c(-9,-4,0) ~ 0,
       TRUE ~ NA_real_
     ),
     union = case_when( # 1 = member
       union %in% c(1,2) ~ 1,
       union %in% c(3,-9,-7,-4) ~ 0,
       TRUE ~ NA_real_
     ),
    sparent = case_when(
      marital %in% c(3:6) & ((hhchildr > 0 & hhchildr < 96) | (hhtodd >0 & hhtodd <96)) ~ 1,
      marital %in% c(1:2) ~ 0,
      marital %in% c(3:6) & hhchildr == 0 & hhtodd == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    wrkst = case_when( # different from other years, make similar
       mainstat == 1 ~ 1,
       mainstat == 2 ~ 5,
       mainstat == 3 ~ 6,
       mainstat == 4 ~ 6,
       mainstat == 5 ~ 9,
       mainstat == 6 ~ 7,
       mainstat == 7 ~ 8,
       mainstat == 8 ~ 10,
       mainstat == 9 ~ 10,
       TRUE ~ NA_real_
     ),
    nemploy = ifelse(nsup %in% c(-4,-9), NA_real_, nsup),
    selfemp = case_when(emprel %in% c(2,3,4) ~ 1, emprel %in% c(-4,-9) ~ NA_real_, TRUE ~ 0),
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs), # trim workhrs,
    isco88 = occupar::isco08to88(isco08),
    spisco88 = occupar::isco08to88(spisco08)
  ) 

# ISCO88 to EGP

socin3$egp <- occupar::isco88toEGP(isco88 = socin3$isco88, n.employees = socin3$nemploy, self.employed = socin3$selfemp)

# EGP to EGP6
socin3 <- socin3 %>%
  mutate(
    egp6 = car::recode(egp, recodes = '"I     Service class I" = "Service I";"II    Service class II" = "Service II"; "III.a Routine non-manual, higher grade" = "Routine"; "III.b Routine non-manual, lower grade" = "Routine"; "IV.a  Self-employed with employees" = "Self"; "IV.b  Self-employed with no empoyees" = "Self"; "IV.c  Self-employed Farmers etc" = "Self"; "V     Manual supervisors/Lower grade technicians" = "Skilled";"VI    Skilled workers" = "Skilled"; "VII.a Unskilled workers" = "Unskilled"; "VII.b Farm labours" = "Unskilled"')
  )

# ISEI
socin3$isei <- occupar::isco88toISEI92(isco88 = socin3$isco88)


## Respondent's income, scaled.

temp <- socin3 %>% dplyr::select(contains("_rinc"))
temp2 <- temp
temp[temp >= 999990] <- NA
temp <- as.data.frame(lapply(temp, function(x) ntile(x, 10))) # deciles
socin3$rincZ <- rowMeans(temp, na.rm = T)
socin3$rincZ <- ifelse(socin3$rincZ == "NaN", NA, socin3$rincZ)

socin3$rincO <- rowMeans(temp2, na.rm = T)
socin3$rincO <- ifelse(socin3$rincO == "NaN", NA, socin3$rincO)
## Household income, scaled.

temp <- socin3 %>% dplyr::select(contains("_inc"))
temp[temp >= 999990] <- NA
temp <- as.data.frame(lapply(temp, function(x) ntile(x, 10))) # deciles
socin3$hincZ <- rowMeans(temp, na.rm = T)
socin3$hincZ <- ifelse(socin3$hincZ == "NaN", NA, socin3$hincZ)
## Father, mother, and spouse

socin3 <- socin3 %>%
  mutate(
    f_egp = NA_real_,
    f_egp6 = NA_real_,
    f_isei = NA_real_,
    m_egp = NA_real_,
    m_egp6 = NA_real_,
    m_isei = NA_real_,
    fisco88_2digit = NA_real_,
    misco88_2digit = NA_real_
  )

socin3 <- socin3 %>%
  mutate(
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA),
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA),
    hhcycle = NA_real_
  ) # Truncate isco88 and spisco88 values


# Select relevant variables 
socin3 <- dplyr::select(socin3,c(cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit))



```


### Merge



```{r merge_v, include = TRUE, warning=F}
## Merge data sets  


mer1 <- plyr::rbind.fill(dk99,ie99)
mer2 <- plyr::rbind.fill(mer1,nl09)
mer2$rincZ <- as.vector(mer2$rincZ)
mer2$hincZ <- as.vector(mer2$hincZ)
df <- plyr::rbind.fill(mer2,socin)
df$rincz <- as.vector(df$rincZ)
df$hincZ <- as.vector(df$hincZ)
df <- plyr::rbind.fill(df, socin3)
df <- df %>%
  group_by(cntry, year) %>%
  mutate(
    rincO = zap_labels(rincO)
  )

```

## Data transformation - Environment 93

Occupation codes are mixed:

Respondent's Occupation: ILO/ ISCO - International Code 1968

CDN,IL,E,NZ: Present job - ILO/ISCO 1968
D,N,BG,CZ: Present or last job - ILO/ISCO 1968
USA,H: Present or last job - 4-digit ILO/ISCO 1968
AUS,IRL,SLO,PL:Present or last occupation - *ISCO 1988*   
RUS: Present main job - *ISCO 1988*

### Missing
99997. Refused
99998. Not classifiable; inadequately described, DK
99999. NA
00000. NAP (not in labour force, never had a job)
Not available


```{r env93, include = TRUE, warning=F,message=F}

env93 <- env93 %>%
  mutate(
    cntry = zap_labels(v3),
    cntry = dplyr::recode(cntry, `1` = 36, `2` = 276, `3` = 276, `4` = 826, `5` = 826, `6` = 840, `8` = 348, `9` = 380,
                          `10` = 372, `11` = 528, `12` = 578, `13` = 203, `14` = 705, `15` = 616, `16` = 100, `17` = 643,
                          `18` = 554, `19` = 124, `20` = 608, `21` = 376, `22` = 392, `23` = 724),
    year = 1993,
    wave = 1993,
    female = ifelse(v200 == 9, NA, v200 - 1),
    age = v201,
    incdiff = v6,
    inclarge = NA_real_,
    ageC = ifelse(age > 75, 75, age),
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,        # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    marital = v202,
    married = case_when( # married = 1. Note: using if_else will confound NA with not married (0), make sure life partners are coded as married
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
     ),
    educyrs = v204,
# It's a little problematic here because in GB or AUS, they cut at 14 and 20     
    educyrs = case_when(
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8,
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
      v330 %in% c(2,3,4,6,7,8,10,12,14,16,18,20,22,24,26,28) ~ 1,
      v330 %in% c(1,5,9,11,13,15,17,19,21,23,25,27,95) ~ 0,
      TRUE ~ NA_real_ 
    ),
    degree = v205, ## need to be recoded. But how?
    union = case_when(
      v279 == 2 ~ 0,
      v279 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      v330 %in% c(2,3,4) ~ 1,
      v330 %in% c(1,5:95) ~ 0,
      TRUE ~ NA_real_
    ),
    wrkhrs = v224, 
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    wrkst = ifelse(v212 == 4, 8, v212),
    selfemp = ifelse(v221 %in% c(0,9), NA_real_, abs(v221-2)), ## self-employed = 1,
    v222 = zap_labels(v222),
    nemploy = case_when(v222 == 9996 ~ 0, v222 %in% c(0,9998,9999) ~ NA_real_, TRUE ~ v222)
  )
# Occupation codes


# Australia, Ireland, Slovakia, Poland and Russia are in isco88 format already

 env93 <- env93 %>%
  mutate(
    isco68 = ifelse(cntry!= 36 & cntry != 372 & cntry != 705 & cntry!=616 & cntry!=643, as.numeric(v214), NA),
    isco88_2 = as.numeric(v214),
    fisco68 = ifelse(cntry!= 36 & cntry != 372 & cntry != 705 & cntry!=616 & cntry!=643, as.numeric(v219), NA),
    fisco88_2 = as.numeric(v219),
    misco68 = ifelse(cntry!= 36 & cntry != 372 & cntry != 705 & cntry!=616 & cntry!=643, as.numeric(v218), NA),
    misco88_2 = as.numeric(v218),
    spisco68 = ifelse(cntry!= 36 & cntry != 372 & cntry != 705 & cntry!=616 & cntry!=643, as.numeric(v216), NA),
    spisco88_2 = as.numeric(v216)
  )


# ISCO68 problems


# In Germany, Norway, Czech Republic, BUlgaria, Canada, Israel, New Zealand, and Spain, isco68 appears to be 3-digit, multiply by 10 and add 1 to translate to 4-digit. 


env93$isco68 <- ifelse(env93$cntry %in% c(276,100,124,376,554,578,705,724), (env93$isco68 * 10)+1, env93$isco68)
env93$fisco68 <- ifelse(env93$cntry %in% c(276,100,124,376,554,578,705,724), (env93$fisco68 * 10)+1, env93$fisco68)
env93$misco68 <- ifelse(env93$cntry %in% c(276,100,124,376,554,578,705,724), (env93$misco68 * 10)+1, env93$misco68)
env93$spisco68 <- ifelse(env93$cntry %in% c(276,100,124,376,554,578,705,724), (env93$spisco68 * 10)+1, env93$spisco68)
  

# Norway: Nordic Standard Classification of Occupation (20: Chief Engineers = 230: Electrical and electronics engineers)
env93[which(env93$cntry==578),]$isco68 <- car::recode(env93[which(env93$cntry==578),]$isco68, recodes = '20 = 230')
env93[which(env93$cntry==578),]$spisco68 <- car::recode(env93[which(env93$cntry==578),]$spisco68, recodes = '20 = 230')

# Create Isco88 vector


env93$isco88 <- occupar::isco68to88(isco68 = env93$isco68, display.nas = T)
env93$fisco88 <- occupar::isco68to88(isco68 = env93$fisco68, display.nas = T)
env93$misco88 <- occupar::isco68to88(isco68 = env93$misco68, display.nas = T)
env93$spisco88 <- occupar::isco68to88(isco68 = env93$spisco68, display.nas = T)


# Slovenia

# Philippines

# Netherlands 

# Israel

# Japan  - Self 
env93$jp_occ <- env93$isco68
env93$jp_occ <- car::recode(env93$jp_occ, recodes = "7 = 2265; 8 = 2265; 5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233;
                            9  = NA; 10= NA; 11 = NA")
env93[which(env93$cntry == 392),]$isco88 <- env93[which(env93$cntry == 392),]$jp_occ
jp_occ <- env93[which(env93$cntry == 392),]$isco88 
educyrsjp <- env93[which(env93$cntry == 392),]$educyrs
jp <- as.data.frame(cbind(jp_occ, educyrsjp))
jp$jp_occ <- if_else(jp$jp_occ == 4115 & jp$educyrsjp < 14, 3416, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 7233 & jp$educyrsjp > 11, 4211, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 6130 & jp$educyrsjp < 12, 9211, jp$jp_occ)
jp$jp_occ <- if_else(jp$jp_occ == 2265 & jp$educyrsjp < 16, 1229, jp$jp_occ)
env93[which(env93$cntry == 392),]$isco88 <- jp$jp_occ

# Japan - Father 

env93$jp_focc <- env93$fisco68
env93$jp_focc <- car::recode(env93$jp_focc, recodes = "7 = 2265; 8 = 2265; 5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233;
                            9  = NA; 10= NA; 11 = NA")
env93[which(env93$cntry == 392),]$fisco88 <- env93[which(env93$cntry == 392),]$jp_focc
jp_focc <- env93[which(env93$cntry == 392),]$fisco88 
feducyrsjp <- env93[which(env93$cntry == 392),]$v210
jp <- as.data.frame(cbind(jp_focc, feducyrsjp))
jp$jp_focc <- if_else(jp$jp_focc == 4115 & jp$feducyrsjp < 14, 3416, jp$jp_focc)
jp$jp_focc <- if_else(jp$jp_focc == 7233 & jp$feducyrsjp > 11, 4211, jp$jp_focc)
jp$jp_focc <- if_else(jp$jp_focc == 6130 & jp$feducyrsjp < 12, 9211, jp$jp_focc)
jp$jp_focc <- if_else(jp$jp_focc == 2265 & jp$feducyrsjp < 16, 1229, jp$jp_focc)
env93[which(env93$cntry == 392),]$fisco88 <- jp$jp_focc


# Japan - Mother 

env93$jp_mocc <- env93$misco68
env93$jp_mocc <- car::recode(env93$jp_mocc, recodes = "7 = 2265; 8 = 2265; 5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233;
                            9  = NA; 10= NA; 11 = NA")
env93[which(env93$cntry == 392),]$misco88 <- env93[which(env93$cntry == 392),]$jp_mocc
jp_mocc <- env93[which(env93$cntry == 392),]$misco88 
meducyrsjp <- env93[which(env93$cntry == 392),]$v208
jp <- as.data.frame(cbind(jp_mocc, meducyrsjp))
jp$jp_mocc <- if_else(jp$jp_mocc == 4115 & jp$meducyrsjp < 14, 3416, jp$jp_mocc)
jp$jp_mocc <- if_else(jp$jp_mocc == 7233 & jp$meducyrsjp > 11, 4211, jp$jp_mocc)
jp$jp_mocc <- if_else(jp$jp_mocc == 6130 & jp$meducyrsjp < 12, 9211, jp$jp_mocc)
jp$jp_mocc <- if_else(jp$jp_mocc == 2265 & jp$meducyrsjp < 16, 1229, jp$jp_mocc)
env93[which(env93$cntry == 392),]$misco88 <- jp$jp_mocc

# Japan - Spouse

env93$jp_socc <- env93$spisco68
env93$jp_socc <- car::recode(env93$jp_socc, recodes = "7 = 2265; 8 = 2265; 5 = 9322; 4 = 7233; 3 = 5130; 6 = 4115; 1 = 6130; 2 = 7233;
                            9  = NA; 10= NA; 11 = NA")
env93[which(env93$cntry == 392),]$spisco88 <- env93[which(env93$cntry == 392),]$jp_socc
jp_socc <- env93[which(env93$cntry == 392),]$spisco88 
seducyrsjp <- env93[which(env93$cntry == 392),]$v206
jp <- as.data.frame(cbind(jp_socc, seducyrsjp))
jp$jp_socc <- if_else(jp$jp_socc == 4115 & jp$seducyrsjp < 14, 3416, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 7233 & jp$seducyrsjp > 11, 4211, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 6130 & jp$seducyrsjp < 12, 9211, jp$jp_socc)
jp$jp_socc <- if_else(jp$jp_socc == 2265 & jp$seducyrsjp < 16, 1229, jp$jp_socc)
env93[which(env93$cntry == 392),]$spisco88 <- jp$jp_socc


# Nation-specific Occ recodes

# Italy goes from 1 to 22, looks similar to 1992, check that this is absolute at some point
# Great Britain: Standard Occupational Classification, this should be SOC80, but make sure someday (it might be SOC90 which means the code below may not work)

env93 <- env93 %>%
  mutate(
    isco88_2digit_it = case_when(
      v215 == 1 & cntry == 380 ~ 13,
      v215 == 2 & cntry == 380 ~ 12,
      v215 == 3 & cntry == 380 ~ 26,
      v215 == 4 & cntry == 380 ~ 11,
      v215 == 5 & cntry == 380 ~ 11,
      v215 == 6 & cntry == 380 ~ 23,
      v215 == 7 & cntry == 380 ~ 34,
      v215 == 8 & cntry == 380 ~ 1,
      v215 == 9 & cntry == 380 ~ 33,
      v215 == 10 & cntry == 380 ~ 41,
      v215 == 11 & cntry == 380 ~ 26,
      v215 == 12 & cntry == 380 ~ 81,
      v215 == 13 & cntry == 380 ~ 2,
      v215 == 14 & cntry == 380 ~ 91,
      v215 == 15 & cntry == 380 ~ 92,
      v215 == 16 & cntry == 380 ~ 24,
      v215 == 17 & cntry == 380 ~ 52,
      v215 == 18 & cntry == 380 ~ 71,
      v215 == 19 & cntry == 380 ~ 95,
      v215 == 20 & cntry == 380 ~ 91,
      v215 == 21 & cntry == 380 ~ 61,
      v215 == 22 & cntry == 380 ~ 91,
      v215 == 10 & cntry == 826 ~ 11,
      v215 == 11 & cntry == 826 ~ 13,
      v215 == 12 & cntry == 826 ~ 13,
      v215 == 13 & cntry == 826 ~ 12,
      v215 == 14 & cntry == 826 ~ 24,
      v215 == 15 & cntry == 826 ~ 54,
      v215 == 16 & cntry == 826 ~ 12,
      v215 == 17 & cntry == 826 ~ 14,
      v215 == 19 & cntry == 826 ~ 14,
      v215 == 20 & cntry == 826 ~ 21,
      v215 == 21 & cntry == 826 ~ 21,
      v215 == 22 & cntry == 826 ~ 22,
      v215 == 23 & cntry == 826 ~ 23,
      v215 == 24 & cntry == 826 ~ 26,
      v215 == 25 & cntry == 826 ~ 24,
      v215 == 26 & cntry == 826 ~ 21,
      v215 == 27 & cntry == 826 ~ 25,
      v215 == 29 & cntry == 826 ~ 34,
      v215 == 30 & cntry == 826 ~ 31,
      v215 == 31 & cntry == 826 ~ 31,
      v215 == 32 & cntry == 826 ~ 35,
      v215 == 33 & cntry == 826 ~ 33,
      v215 == 34 & cntry == 826 ~ 32,
      v215 == 35 & cntry == 826 ~ 34,
      v215 == 36 & cntry == 826 ~ 33,
      v215 == 37 & cntry == 826 ~ 34,
      v215 == 38 & cntry == 826 ~ 34,
      v215 == 39 & cntry == 826 ~ 31,
      v215 == 40 & cntry == 826 ~ 44,
      v215 == 41 & cntry == 826 ~ 43,
      v215 == 42 & cntry == 826 ~ 43,
      v215 == 43 & cntry == 826 ~ 44,
      v215 == 44 & cntry == 826 ~ 42,
      v215 == 45 & cntry == 826 ~ 51,
      v215 == 46 & cntry == 826 ~ 51,
      v215 == 49 & cntry == 826 ~ 51,
      v215 == 50 & cntry == 826 ~ 71,
      v215 == 51 & cntry == 826 ~ 72,
      v215 == 52 & cntry == 826 ~ 74,
      v215 == 53 & cntry == 826 ~ 72,
      v215 == 54 & cntry == 826 ~ 72,
      v215 == 55 & cntry == 826 ~ 75,
      v215 == 56 & cntry == 826 ~ 75,
      v215 == 57 & cntry == 826 ~ 75,
      v215 == 58 & cntry == 826 ~ 75,
      v215 == 59  & cntry == 826 ~ 75,
      v215 == 60  & cntry == 826 ~ 1,
      v215 == 61  & cntry == 826 ~ 54,
      v215 == 62  & cntry == 826 ~ 52,
      v215 == 63  & cntry == 826 ~ 52,
      v215 == 64  & cntry == 826 ~ 14,
      v215 == 65  & cntry == 826 ~ 51,
      v215 == 66  & cntry == 826 ~ 51,
      v215 == 67  & cntry == 826 ~ 91,
      v215 == 69  & cntry == 826 ~ 54,
      v215 == 70  & cntry == 826 ~ 52,
      v215 == 71  & cntry == 826 ~ 52,
      v215 == 72  & cntry == 826 ~ 95,
      v215 == 73  & cntry == 826 ~ 95,
      v215 == 79  & cntry == 826 ~ 95,
      v215 == 80  & cntry == 826 ~ 94,
      v215 == 81  & cntry == 826 ~ 82,
      v215 == 82  & cntry == 826 ~ 81,
      v215 == 83  & cntry == 826 ~ 81,
      v215 == 84  & cntry == 826 ~ 81,
      v215 == 85  & cntry == 826 ~ 82,
      v215 == 86  & cntry == 826 ~ 82,
      v215 == 87  & cntry == 826 ~ 83,
      v215 == 88  & cntry == 826 ~ 83,
      v215 == 89  & cntry == 826 ~ 81,
      v215 == 90  & cntry == 826 ~ 92,
      v215 == 91  & cntry == 826 ~ 93,
      v215 == 92  & cntry == 826 ~ 93,
      v215 == 93  & cntry == 826 ~ 93,
      v215 == 94  & cntry == 826 ~ 95,
      v215 == 95  & cntry == 826 ~ 95,
      v215 == 99  & cntry == 826 ~ 96,
      TRUE ~ NA_real_
    )
  )

env93 <- env93 %>%
  mutate(
    spisco88_2digit_gbr = case_when(
      v217 == 1 & cntry == 380 ~ 13,
      v217 == 2 & cntry == 380 ~ 12,
      v217 == 3 & cntry == 380 ~ 26,
      v217 == 4 & cntry == 380 ~ 11,
      v217 == 5 & cntry == 380 ~ 11,
      v217 == 6 & cntry == 380 ~ 23,
      v217 == 7 & cntry == 380 ~ 34,
      v217 == 8 & cntry == 380 ~ 1,
      v217 == 9 & cntry == 380 ~ 33,
      v217 == 10 & cntry == 380 ~ 41,
      v217 == 11 & cntry == 380 ~ 26,
      v217 == 12 & cntry == 380 ~ 81,
      v217 == 13 & cntry == 380 ~ 2,
      v217 == 14 & cntry == 380 ~ 91,
      v217 == 15 & cntry == 380 ~ 92,
      v217 == 16 & cntry == 380 ~ 24,
      v217 == 17 & cntry == 380 ~ 52,
      v217 == 18 & cntry == 380 ~ 71,
      v217 == 19 & cntry == 380 ~ 95,
      v217 == 20 & cntry == 380 ~ 91,
      v217 == 21 & cntry == 380 ~ 61,
      v217 == 22 & cntry == 380 ~ 91,
      v217 == 11 & cntry == 826 ~ 13,
      v217 == 12 & cntry == 826 ~ 13,
      v217 == 13 & cntry == 826 ~ 12,
      v217 == 14 & cntry == 826 ~ 24,
      v217 == 15 & cntry == 826 ~ 54,
      v217 == 16 & cntry == 826 ~ 12,
      v217 == 17 & cntry == 826 ~ 14,
      v217 == 19 & cntry == 826 ~ 14,
      v217 == 20 & cntry == 826 ~ 21,
      v217 == 21 & cntry == 826 ~ 21,
      v217 == 22 & cntry == 826 ~ 22,
      v217 == 23 & cntry == 826 ~ 23,
      v217 == 24 & cntry == 826 ~ 26,
      v217 == 25 & cntry == 826 ~ 24,
      v217 == 26 & cntry == 826 ~ 21,
      v217 == 27 & cntry == 826 ~ 25,
      v217 == 29 & cntry == 826 ~ 34,
      v217 == 30 & cntry == 826 ~ 31,
      v217 == 31 & cntry == 826 ~ 31,
      v217 == 32 & cntry == 826 ~ 35,
      v217 == 33 & cntry == 826 ~ 33,
      v217 == 34 & cntry == 826 ~ 32,
      v217 == 35 & cntry == 826 ~ 34,
      v217 == 36 & cntry == 826 ~ 33,
      v217 == 37 & cntry == 826 ~ 34,
      v217 == 38 & cntry == 826 ~ 34,
      v217 == 39 & cntry == 826 ~ 31,
      v217 == 40 & cntry == 826 ~ 44,
      v217 == 41 & cntry == 826 ~ 43,
      v217 == 42 & cntry == 826 ~ 43,
      v217 == 43 & cntry == 826 ~ 44,
      v217 == 44 & cntry == 826 ~ 42,
      v217 == 45 & cntry == 826 ~ 51,
      v217 == 46 & cntry == 826 ~ 51,
      v217 == 49 & cntry == 826 ~ 51,
      v217 == 50 & cntry == 826 ~ 71,
      v217 == 51 & cntry == 826 ~ 72,
      v217 == 52 & cntry == 826 ~ 74,
      v217 == 53 & cntry == 826 ~ 72,
      v217 == 54 & cntry == 826 ~ 72,
      v217 == 55 & cntry == 826 ~ 75,
      v217 == 56 & cntry == 826 ~ 75,
      v217 == 57 & cntry == 826 ~ 75,
      v217 == 58 & cntry == 826 ~ 75,
      v217 == 59  & cntry == 826 ~ 75,
      v217 == 60  & cntry == 826 ~ 1,
      v217 == 61  & cntry == 826 ~ 54,
      v217 == 62  & cntry == 826 ~ 52,
      v217 == 63  & cntry == 826 ~ 52,
      v217 == 64  & cntry == 826 ~ 14,
      v217 == 65  & cntry == 826 ~ 51,
      v217 == 66  & cntry == 826 ~ 51,
      v217 == 67  & cntry == 826 ~ 91,
      v217 == 69  & cntry == 826 ~ 54,
      v217 == 70  & cntry == 826 ~ 52,
      v217 == 71  & cntry == 826 ~ 52,
      v217 == 72  & cntry == 826 ~ 95,
      v217 == 73  & cntry == 826 ~ 95,
      v217 == 79  & cntry == 826 ~ 95,
      v217 == 80  & cntry == 826 ~ 94,
      v217 == 81  & cntry == 826 ~ 82,
      v217 == 82  & cntry == 826 ~ 81,
      v217 == 83  & cntry == 826 ~ 81,
      v217 == 84  & cntry == 826 ~ 81,
      v217 == 85  & cntry == 826 ~ 82,
      v217 == 86  & cntry == 826 ~ 82,
      v217 == 87  & cntry == 826 ~ 83,
      v217 == 88  & cntry == 826 ~ 83,
      v217 == 89  & cntry == 826 ~ 81,
      v217 == 90  & cntry == 826 ~ 92,
      v217 == 91  & cntry == 826 ~ 93,
      v217 == 92  & cntry == 826 ~ 93,
      v217 == 93  & cntry == 826 ~ 93,
      v217 == 94  & cntry == 826 ~ 95,
      v217 == 95  & cntry == 826 ~ 95,
      v217 == 99  & cntry == 826 ~ 96,
      TRUE ~ NA_real_
    )
  )


# Slovenia - Father + Mother


# Coalesce


env93$isco88 <- coalesce(env93$isco88,env93$isco88_2)
env93$fisco88 <- coalesce(env93$fisco88,env93$fisco88_2)
env93$misco88 <- coalesce(env93$misco88,env93$misco88_2)
env93$spisco88 <- coalesce(env93$spisco88,env93$spisco88_2)

# ISCO88 to EGP/EGP6 and ISEI

env93 <- env93 %>%
  mutate(
    egp  = occupar::isco88toEGP(isco88 = isco88, n.employees = nemploy, self.employed = selfemp),
    egp6 = car::recode(egp, recodes = egp6),
    isei = occupar::isco88toISEI92(isco88 = isco88),
    f_egp = occupar::isco88toEGP(fisco88, NULL, NULL),
    f_egp6 = car::recode(f_egp, recodes = egp6_2),
    f_isei = occupar::isco88toISEI92(fisco88),
    m_egp = occupar::isco88toEGP(misco88, NULL, NULL),
    m_egp6 = car::recode(m_egp, recodes = egp6_2),
    m_isei = occupar::isco88toISEI92(misco88)
  )





# 2 Digits

env93 <- env93 %>%
  mutate(
    isco88_2digit_else = ifelse(!is.na(isco88), trunc(isco88/100), NA),
    isco88_2digit = coalesce(isco88_2digit_it, isco88_2digit_else),
    fisco88_2digit = ifelse(!is.na(fisco88), trunc(fisco88/100), NA),
    misco88_2digit = ifelse(!is.na(misco88), trunc(misco88/100), NA),
    spisco88_2digit_else = ifelse(!is.na(spisco88), trunc(spisco88/100), NA),
    spisco88_2digit = coalesce(spisco88_2digit_gbr, spisco88_2digit_else)
    ) 

## Earnings - grouped by country, then deciles

env93 <- env93 %>%
  group_by(cntry) %>%
  mutate(
    rincZ = ntile(v231, 10),
    rincO = v231,
    hincZ = ntile(v253, 10)
  ) %>%
  ungroup()

# Select relevant variables 

env93 <- dplyr::select(env93,c(cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit))

```


## Data transformation - Environment 2000

```{r env00, include = TRUE, warning=F,message=F}
env00 <- env00 %>%
  mutate(
    cntry = zap_labels(v3),
    cntry = dplyr::recode(cntry, `1` = 36, `2` = 276, `3` = 276, `4` = 826, `5` = 826, `6` = 840, `7` = 40, `8` = 348,
                          `9` = 380, `10` = 372, `11` = 528, `12` = 578, `13` = 752, `14` = 203, `15` = 705, `16` = 616,
                          `17` = 100, `18` = 643, `19` = 554, `20` = 124, `21` = 608, `22` = 376, `24` = 392, `25` = 724,
                          `26` = 428, `30` = 620, `31` = 152, `32` = 208, `33` = 756, `37` = 246, `38` = 484),
    year = 2000,
    wave = 2000,
    female = ifelse(v200 == 9, NA, v200 - 1),
    age = v201,
    incdiff = v5,
    inclarge = NA_real_,
    ageC = ifelse(age > 75, 75, age), # trim at 75  
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,         # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    marital = v202,
    married = case_when( # married = 1. Note: using if_else will confound NA with not married (0), make sure life partners are coded as married
       marital %in% c(1:2) ~ 1, # widowed = married
       marital %in% c(3:5) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
     ),
    educyrs = v204,
    educyrs = case_when(
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8,
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
      v273 %in% c(2,3,4,6,7,8,10,12,14,16,18,20,22,24,26,28) ~ 1,
      v273 %in% c(1,5,9,11,13,15,17,19,21,23,25,27,95) ~ 0,
      TRUE ~ NA_real_ 
    ),
    degree = v205, ## need to be recoded. But how?
    union = case_when(
      v245 %in% c(2,3) ~ 0,
      v245 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      v273 %in% c(2,3,4) ~ 1,
      v273 %in% c(1, 5:95) ~ 0,
      TRUE ~ NA_real_
    ),
    wrkhrs = v238,
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    wrkst = ifelse(v231 == 4, 8, v231),
    isco88 = v233,
    spisco88 = v234,
    selfemp = case_when(v236 == 1 ~ 1, v236 %in% c(0,2) ~ 0, TRUE ~ NA_real_),
    nemploy = case_when(v237 == 9995 ~ 0, v237 %in% c(0,9997,9998,9999) ~ NA_real_)
  )
# ISCO88 to EGP


env00$egp <- occupar::isco88toEGP(isco88 = env00$v233, n.employees = env00$nemploy, self.employed = env00$selfemp)

# EGP to EGP6
env00 <- env00 %>%
  mutate(
    egp6 = car::recode(egp, recodes = '"I     Service class I" = "Service I";"II    Service class II" = "Service II"; "III.a Routine non-manual, higher grade" = "Routine"; "III.b Routine non-manual, lower grade" = "Routine"; "IV.a  Self-employed with employees" = "Self"; "IV.b  Self-employed with no empoyees" = "Self"; "IV.c  Self-employed Farmers etc" = "Self"; "V     Manual supervisors/Lower grade technicians" = "Skilled";"VI    Skilled workers" = "Skilled"; "VII.a Unskilled workers" = "Unskilled"; "VII.b Farm labours" = "Unskilled"')
  )

# ISEI
env00$isei <- occupar::isco88toISEI92(isco88 = env00$v233)


## Earnings - grouped by country, then scaled.

env00 <- env00 %>%
  group_by(cntry) %>%
  mutate(
    rincZ = ntile(v240, 10),
    rincO = v240,
    hincZ = ntile(v241, 10)
  ) %>%
  ungroup()
## Father's occupation + Mother's occupation - Not available

env00 <- env00 %>%
  mutate(
    f_egp = NA_real_,
    f_egp6 = NA_real_,
    f_isei = NA_real_,
    m_egp = NA_real_,
    m_egp6 = NA_real_,
    m_isei = NA_real_,
    fisco88_2digit = NA_real_,
    misco88_2digit = NA_real_
  )

env00 <- env00 %>%
  mutate(
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA),
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)  
  ) # Truncate isco88 values

# Select relevant variables 
env00 <- dplyr::select(env00,c(cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit)) 
```


## Data transformation - Environment 2010
```{r env10, include = TRUE, warning=F,message=F}
colnames(env10) <- tolower(colnames(env10))
env10 <- env10 %>%
  mutate(
    cntry = country,
    year = 2010,
    wave = 2010,
    female = ifelse(sex == 9, NA, sex - 1),
    incdiff = v8,
    inclarge = NA_real_,
    ageC = ifelse(age > 75, 75, age), # trim at 75  
    age = case_when(                 # trim at 75     
       age %in% c(16:24) ~ 1,         # Changed to 7 categories
       age %in% c(25:34) ~ 2,
       age %in% c(35:44) ~ 3,
       age %in% c(45:54) ~ 4,
       age %in% c(55:64) ~ 5,
       age %in% c(65:74) ~ 6,
       age >= 75 ~ 7,
       TRUE ~ NA_real_
     ),
    married = case_when( # married = 1. widowed and civil partnership = married 
       marital %in% c(1,2,5) ~ 1, # widowed = married
       marital %in% c(3,4,6) ~ 0, # divorced, separated = not married
       TRUE ~ NA_real_
     ),
    educyrs = case_when(  
       educyrs > 22 & educyrs < 95 ~ 23, 
       educyrs == 95 ~ 8,
       educyrs == 96 ~ 13,
       educyrs %in% c(97:99) ~ NA_real_,
       TRUE ~ as.numeric(educyrs)
    ),
    child = case_when(
       hhchildr %in% c(1:9) | hhtodd %in% c(1:9) ~ 1,
       hhchildr == 0 & hhtodd == 0 ~ 0,
       TRUE ~ NA_real_
    ),
    selfemp = case_when(
      emprel %in% c(2:4) ~ 1,
      emprel == 1 ~ 0,
      TRUE ~ NA_real_
    ),
    union = case_when(
      union %in% c(2,3) ~ 0,
      union == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    sparent = case_when(
      marital %in% c(3:6) & ((hhchildr > 0 & hhchildr < 96) | (hhtodd >0 & hhtodd <96)) ~ 1,
      marital %in% c(1:2) ~ 0,
      marital %in% c(3:6) & hhchildr == 0 & hhtodd == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    wrkst = case_when(
      mainstat == 1 & wrkhrs > 34 ~ 1,
      mainstat == 1 & (wrkhrs > 14 & wrkhrs < 35) ~ 2,
      mainstat == 1 & wrkhrs < 15 ~ 3,
      mainstat == 2 ~ 5,
      mainstat %in% c(3,4) ~ 6,
      mainstat == 6 ~ 7,
      mainstat == 7  ~ 8, 
      mainstat == 5 ~ 9,
      mainstat %in% c(8,9) ~ 10,
      TRUE ~ NA_real_
    ),
    wrkhrs = ifelse(wrkhrs > 59, 60, wrkhrs),
    nemploy = ifelse(nemploy %in% c(0,9999), NA_real_, nemploy)
  ) 

# ISCO88 to EGP


env10$egp <- occupar::isco88toEGP(isco88 = env10$isco88, n.employees = env10$nemploy, self.employed = env10$selfemp)

# EGP to EGP6
env10 <- env10 %>%
  mutate(
    egp6 = car::recode(egp, recodes = '"I     Service class I" = "Service I";"II    Service class II" = "Service II"; "III.a Routine non-manual, higher grade" = "Routine"; "III.b Routine non-manual, lower grade" = "Routine"; "IV.a  Self-employed with employees" = "Self"; "IV.b  Self-employed with no empoyees" = "Self"; "IV.c  Self-employed Farmers etc" = "Self"; "V     Manual supervisors/Lower grade technicians" = "Skilled";"VI    Skilled workers" = "Skilled"; "VII.a Unskilled workers" = "Unskilled"; "VII.b Farm labours" = "Unskilled"')
  )

# ISEI
env10$isei <- occupar::isco88toISEI92(isco88 = env10$isco88)


## Respondent's income, scaled.

temp <- dplyr::select(env10, ar_rinc:za_rinc)
temp2 <- temp
temp[temp >= 999990] <- NA
temp <- as.data.frame(lapply(temp, function(x) ntile(x, 10))) # deciles
env10$rincZ <- rowMeans(temp, na.rm = T)
env10$rincZ <- ifelse(env10$rincZ == "NaN", NA, env10$rincZ)

env10$rincO <- rowMeans(temp2, na.rm = T)
env10$rincO <- ifelse(env10$rincO == "NaN", NA, env10$rincO)
## Household income, scaled.

temp <- dplyr::select(env10, ar_inc:za_inc)
temp[temp >= 999990] <- NA
temp <- as.data.frame(lapply(temp, function(x) ntile(x, 10))) # deciles
env10$hincZ <- rowMeans(temp, na.rm = T)
env10$hincZ <- ifelse(env10$hincZ == "NaN", NA, env10$hincZ)

## Father's occupation + Mother's occupation - Not available

env10 <- env10 %>%
  mutate(
    f_egp = NA_real_,
    f_egp6 = NA_real_,
    f_isei = NA_real_,
    m_egp = NA_real_,
    m_egp6 = NA_real_,
    m_isei = NA_real_,
    fisco88_2digit = NA_real_,
    misco88_2digit = NA_real_
  )

env10 <- env10 %>%
  mutate(
    isco88_2digit = ifelse(!is.na(isco88), trunc(isco88/100), NA),
    spisco88_2digit = ifelse(!is.na(spisco88), trunc(spisco88/100), NA)
  ) # Truncate isco88 and spisco88 values


# Select relevant variables 
env10 <- dplyr::select(env10,c(cntry, year, wave, age, ageC, female, educyrs, degree, child, married, rincZ, hincZ, rincO, isei, egp, egp6, f_egp, f_egp6, f_isei, m_egp, m_egp6, m_isei, union, sparent, wrkhrs, wrkst, incdiff, inclarge, isco88, isco88_2digit, fisco88_2digit, misco88_2digit, spisco88_2digit))

```
## Merge environment data sets and social inequality cumulative data set and save 

```{r mergesave, include = TRUE, warning=F,message=F}
## Merge

env <- plyr::rbind.fill(env93,env00)
env <- plyr::rbind.fill(env,env10)
df <- plyr::rbind.fill(env,df)


## Add and modify a few more variables 

df <- df %>%
  mutate(
         year = ifelse(wave == 1987 & cntry == 40, 1988, 
                       ifelse((wave == 1992 & cntry == 36) | (wave == 1992 & cntry == 40) | (wave == 1992 & cntry == 100), 1993, ifelse(wave == 1987 & cntry == 372, 1989,
                              ifelse(wave == 1992 & cntry == 752, 1991, 
                                     ifelse((wave == 1999 & cntry == 40) |(wave == 1999 & cntry == 152) | (wave == 1999 & cntry == 276) | (wave == 1999 & cntry == 840), 2000, 
                                            ifelse((wave == 1999 & cntry == 348) | (wave == 1999 & cntry == 705), 1998, 
                                                   ifelse((wave == 1999 & cntry == 372) | (wave == 1999 & cntry == 703), 2001, 
                                                          ifelse((wave == 2009 & cntry == 156) | (wave == 2009 & cntry == 203), 2008, 
                                                                 ifelse((wave == 2009 & cntry == 32) | (wave == 2009 & cntry == 36) | (wave == 2009 & cntry == 40) | (wave == 2009 & cntry == 233) | (wave == 2009 & cntry == 233) | (wave == 2009 & cntry == 276) | (wave == 2009 & cntry == 352) | (wave == 2009 & cntry == 616) | (wave == 2009 & cntry == 840) | (wave == 2009 & cntry == 862), 2010, 
                                                                        ifelse((wave == 2009 & cntry == 380) | (wave == 2009 & cntry == 440), 2011, 
                                                                               ifelse(wave == 2009 & cntry == 528, 2013, 
                                                                                      ifelse((wave == 1993 & cntry == 100) | (wave == 1993 & cntry == 724), 1994, 
                                                                                             ifelse(wave == 1993 & cntry == 392, 1992, 
                                                                                                    ifelse((wave == 2000 & cntry == 40) | (wave == 2000 & cntry == 124) | (wave == 2000 & cntry == 208) | (wave == 2000 & cntry == 372) | (wave == 2000 & cntry == 484) | (wave == 2000 & cntry == 752) | (wave == 2000 & cntry == 756), 2001, 
                                                                                                           ifelse((wave == 2010 & cntry == 100) | (wave == 2010 & cntry == 124) | (wave == 2010 & cntry == 191) | (wave == 2010 & cntry == 376) | (wave == 2010 & cntry == 428) | (wave == 2010 & cntry == 484) | (wave == 2010 & cntry == 528) | (wave == 2010 & cntry == 578) | (wave == 2010 & cntry == 705) | (wave == 2010 & cntry == 756), 2011, 
                                                                                                                  ifelse((wave == 2010 & cntry == 352) | (wave == 2010 & cntry == 36) | (wave == 2010 & cntry == 608), 2012, 
                                                                                                                         ifelse((wave == 2010 & cntry == 608) | (wave == 2010 & cntry == 703), 2009, year)))))))))))))))))
  )


# Make a country-year variable
df$cyear <- (df$cntry*10000)+df$year
# Country names
df$country <- countrycode(df$cntry, "iso3n", "country.name")
# Recode IncDiff
df$incdiff <- ifelse(df$incdiff %in% c(8,-8, 9, -9), NA_real_, df$incdiff)
df$inclarge <- ifelse(df$inclarge %in% c(8,-8, 9, -9), NA_real_, df$inclarge)
df$reduce <- car::recode(df$incdiff, recodes = '1 = 5; 2 = 4; 3 = 3; 8 = 3; 4 = 2; 5 = 1')
df$reduce_large <- car::recode(df$inclarge, recodes = '1 = 5; 2 = 4; 3 = 3; 8 = 3; 4 = 2; 5 = 1')

```

### Social Groups

Recodes from

Schwander, Hanna, and Silja Husermann. 2013. Who Is in and Who Is out? A Risk-Based Conceptualization of Insiders and Outsiders: Journal of European Social Policy 23(8):24869.

Stata code here: http://www.schwander-hanna.ch/Data.html

They recode ISCO 4-digit into 2-digit.

Then they create these 'classes' based on 

Oesch, D. (2006) Redrawing the Class Map: Stratification and Institutions in Germany, Britain, Sweden and Switzerland. London: Palgrave Macmillan

1 "Capital accumulators" 
2 "Mixed service functionaires" 
3 "Blue and lower white collar" 
4 "Socio-cultural (semi-)professionals" 
5 "Low service functionaires"

Strangely, their code omits some ISCO 2-digit codes


14	Hospitality, Retail and Other Services Managers

25	Information and Communications Technology Professionals
26	Legal, Social and Cultural Professionals
  
35	Information and Communications Technicians

43	Numerical and Material Recording Clerks
44	Other Clerical Support Workers

53	Personal Care Workers
54	Protective Services Workers

62	Market-oriented Skilled Forestry, Fishery and Hunting Workers
63	Subsistence Farmers, Fishers, Hunters and Gatherers

75	Food Processing, Woodworking, Garment and Other Craft and Related Trades Workers

94	Food Preparation Assistants
95	Street and Related Sales and Services Workers
96	Refuse Workers and Other Elementary Workers


```{r sgroups}


# create Schwander and Haeusermann coding groups

# seems like they made an error, 60 and 61 should probably be 61 and 62 (as there is no 60 in the 2-digit scheme), perhaps similar with 70 instead of 71 and onwards, 80 instead of 81 and onwards

df <- df %>%
  mutate(sh_groups = case_when(
    isco88_2digit==11 | isco88_2digit==12 | isco88_2digit==13 | isco88_2digit==21 | isco88_2digit==22 | isco88_2digit==24 | isco88_2digit==34 ~ 1,
    isco88_2digit==31 | isco88_2digit==41 | isco88_2digit==42 ~ 2,
    isco88_2digit==60 | isco88_2digit==61 | isco88_2digit==70 | isco88_2digit==71 | isco88_2digit==72 | isco88_2digit==73 | isco88_2digit==74 | isco88_2digit==80 | isco88_2digit==81 | isco88_2digit==82 | isco88_2digit==83 | isco88_2digit==92 | isco88_2digit==93 ~ 3,
    isco88_2digit==23 | isco88_2digit==32 | isco88_2digit==33 ~ 4,
    isco88_2digit==51 | isco88_2digit==52 | isco88_2digit==91 ~ 5)
  )

# Our updated coding scheme
# added 94 & 96 to blue-collar (3)
# added 95 & 53 to low service (5)
# added 14 to mixed service (2)

df <- df %>%
  mutate(sh_groups_new = case_when(
    isco88_2digit==11 | isco88_2digit==12 | isco88_2digit==13 | isco88_2digit==21 | isco88_2digit==22 | isco88_2digit==24 | isco88_2digit==34 ~ 1,
    isco88_2digit==31 | isco88_2digit==41 | isco88_2digit==42 | isco88_2digit==14 ~ 2,
    isco88_2digit==60 | isco88_2digit==61 | isco88_2digit==70 | isco88_2digit==71 | isco88_2digit==72 | isco88_2digit==73 | isco88_2digit==74 | isco88_2digit==80 | isco88_2digit==81 | isco88_2digit==82 | isco88_2digit==83 | isco88_2digit==92 | isco88_2digit==93 | isco88_2digit==94 | isco88_2digit==96 ~ 3,
    isco88_2digit==23 | isco88_2digit==32 | isco88_2digit==33 ~ 4,
    isco88_2digit==51 | isco88_2digit==52 | isco88_2digit==91 | isco88_2digit==95 | isco88_2digit==53 ~ 5)
  )

# Create dummies

df <- df %>%
  mutate(sh_groups_1 = ifelse(sh_groups == 1, 1, ifelse(is.na(sh_groups), NA, 0)),
         sh_groups_2 = ifelse(sh_groups == 2, 1, ifelse(is.na(sh_groups), NA, 0)),
         sh_groups_3 = ifelse(sh_groups == 3, 1, ifelse(is.na(sh_groups), NA, 0)),
         sh_groups_4 = ifelse(sh_groups == 4, 1, ifelse(is.na(sh_groups), NA, 0)),
         sh_groups_5 = ifelse(sh_groups == 5, 1, ifelse(is.na(sh_groups), NA, 0))
  )

df <- df %>%
  mutate(sh_groups_new_1 = ifelse(sh_groups_new == 1, 1, ifelse(is.na(sh_groups_new), NA, 0)),
         sh_groups_new_2 = ifelse(sh_groups_new == 2, 1, ifelse(is.na(sh_groups_new), NA, 0)),
         sh_groups_new_3 = ifelse(sh_groups_new == 3, 1, ifelse(is.na(sh_groups_new), NA, 0)),
         sh_groups_new_4 = ifelse(sh_groups_new == 4, 1, ifelse(is.na(sh_groups_new), NA, 0)),
         sh_groups_new_5 = ifelse(sh_groups_new == 5, 1, ifelse(is.na(sh_groups_new), NA, 0))
  )

```



Save

```{r save}

# clean up variables

## Save df
save(df, file = here::here("data","socstat.Rda"))
```






  



























