---
title: "Analysis NHST"
output:
  html_document:
    df_print: paged
---

TO DO:

Nate - get newer measure of socx from OECD, other macro-level variables (GDP in particular)


##### ISSP, Social Inequality, Cumulation (1987, 1992, 1999, 2009 & 2019)

$~$
$~$

#### **Nate Breznau, Lisa Heukamp, Hung H.V. Nguyen, Tom Knuf, Arne Köller, Sören Goldenstein**
#### **University of Bremen**

_____________________________________________________________________________

$~$
$~$





```{r setup, include=FALSE}
library(pacman)
pacman::p_load("tidyverse", "ggpubr", 
               "ragg", "kableExtra", 
               "lme4", "ggrepel", 
               "sjPlot",
               "arm",
               "margins",
               "ggeffects",
               "modelsummary")

knitr::opts_chunk$set(message = F, warning = F)

```


```{r load dfs}
#df <- readRDS(here::here("data","df.RDS"))
df_na <- readRDS(here::here("data", "df_na.RDS"))
df_macro <- readRDS(here::here("data", "df_macro.RDS"))

```

### Macro-Correlations

```{r macro_corrs}
macro_corr <- df_macro %>% 
  dplyr::select(gov_redist, incdiff_large, corrupt_top_r, corr, 
         libZ, libZ_i, lib_redistZ, lib_redistZ_i, 
         noconf_govZ, noconf_govZ_i, cpiZ, cpiZ_i, 
         gdp_pc_10k, socx, pct_fb_i, gini_disp) %>%
  cor(., use = "pairwise.complete.obs") %>%
  round(2)

macro_corr[upper.tri(macro_corr)] <- ""

write.csv(macro_corr, here::here("results","Tbl2.csv"), row.names = F)
```


### All Plausible Models

#### Moderation models, for specification curve

Selection point. If we've run the models and the margins command before then this will not be necessary. 

NOTE: that if we make changes to the models we have to turn off the selector and re-run, or delete the df_ame file, or the if selection won't work!

```{r ameload}
if (file.exists(here::here("data", "df_ame.RDS"))) { 
  # select if this margins datafile is already there

   df_ame <- readRDS(here::here("data", "df_ame.RDS"))

    } else 
 { source(here::here("data", "Models_nomain.R"))
   model_list <- mget(ls(pattern = "M_"))
   #model_list_lm <- mget(ls(pattern = "L_"))
#########
   # Compile all M_ models margins (multilevel)   
   df_ame <- as.data.frame(matrix(nrow = length(model_list), ncol = 3))

colnames(df_ame) <- c("Model", "mod_b", "mod_se")

model_names <- names(model_list)

for (m in 1:length(model_list)) {
  
  #mn <- as.name(model_names[m])
  
  df_ame[m,1] <- paste(as.character(model_list[[m]]@call), sep = "", collapse = "")
  
  temp <- as.data.frame(summary(get(model_names[m]))[["coefficients"]])
  
  temp <- temp[grepl('cpiZ|noconf_govZ|libZ|corrupt_top|lib_redistZ|incdiff_large|gdp_pc_10k_C', rownames(temp)), 1:2]
  
  df_ame[m,"mod_b"] <- temp[grepl(":", rownames(temp)),1]
  df_ame[m, "mod_se"] <- temp[grepl(":", rownames(temp)),2]
  
}


}
```

#### Get model specifications

```{r ameclean}
df_ame <- df_ame %>%
  mutate(mod_var = ifelse(grepl("noconf_govZ", Model, fixed = T), "B_No_confidence", 
                   ifelse(grepl("cpiZ", Model), "A2_Corruption_percept",
                   ifelse(grepl("corrupt_top", Model), "A1_Corrupt_micro",
         ifelse(grepl("gdp_pc_10k_C:", Model), "C_GDP", NA)))),
         mod_imputed = ifelse(grepl("cpiZ_i|noconf_govZ_i", df_ame$Model), "Yes", "No"),
         ri_cyear = ifelse(grepl("iso3c_wave", df_ame$Model), "Yes", "No"),
         ri_country = ifelse(grepl("iso3c)", df_ame$Model), "Yes", "No"),
         estimation = ifelse(grepl("lmer", df_ame$Model), "GLM", "OLS"),
         control_gdp = ifelse(grepl("gdp", df_ame$Model), "Yes", "No"),
         control_gini = ifelse(grepl("gini", df_ame$Model), "Yes", "No"),
         control_socx = ifelse(grepl("socx", df_ame$Model), "Yes", "No"),
         control_fb = ifelse(grepl("pct_fb", df_ame$Model), "Yes", "No"),
         i_level_control = ifelse(grepl("female", df_ame$Model), "Yes", "No"),
         gdp_m_interaction = ifelse(grepl(":gdp_pc_10k_C", df_ame$Model), "Yes", "No")
         )

df_ame <- df_ame %>%
  arrange(mod_b) %>%
  mutate(count = row_number())

saveRDS(df_ame, here::here("data", "df_ame.RDS"))

```


## Percentage of Agree

Here we compare our heuristics with the percentage of those who do not agree the government should redistribute out of those who agree inequality is too high (the 'inconsistent'
attitude individuals)

### Setup Data

```{r pctagree}
df_tbl <- df_macro %>%
  dplyr::select(iso3c, wave, corr, gap_no_gov, gap_no_gov_opposite, cpiZ_i, noconf_govZ_i, gdp_pc_10k) %>%
  group_by(iso3c,wave) %>%
  summarise_all(mean, na.rm = T) %>%
  ungroup()

df_tbl <- df_tbl %>%
  mutate(gap_no_gov = round(gap_no_gov,1),
         wavea = ifelse(wave > 1999, wave - 2000, wave - 1900),
         wavea = ifelse(wavea == 9, "09", wavea),
         clabs = paste0(iso3c,"'",wavea))
```


### Plot Figs

#### CPI
```{r cpip}
df_tbl %>%
  ggplot(aes(cpiZ_i, gap_no_gov)) +
  geom_text_repel(aes(label = clabs)) +
  geom_smooth(method = lm) +
  labs(x = "Worse Economic Performance (GDPpc)",
       y = "% Inconsistent Attitudes\nDo not agree with gov redistribution") +
  theme_classic()

df_tbl %>%
  ggplot(aes(cpiZ_i, corr)) +
  geom_text_repel(aes(label = clabs)) +
  geom_smooth(method = lm) +
  labs(x = "Worse Economic Performance (GDPpc)",
       y = "% Inconsistent Attitudes\nDo not agree with gov redistribution") +
  theme_classic()

# df_tbl %>%
#   ggplot(aes(cpiZ_i, gap_no_gov_opposite)) +
#   geom_text_repel(aes(label = clabs)) +
#   geom_smooth(method = lm)
  
```

#### No Trust
```{r trust}
df_tbl %>%
  ggplot(aes(noconf_govZ_i, gap_no_gov)) +
  geom_text_repel(aes(label = clabs)) +
  geom_smooth(method = lm) +
  labs(x = "Lack of Trust in Government",
       y = "% Inconsistent Attitudes\nDo not agree with gov redistribution") +
  theme_classic()

# df_tbl %>%
#   ggplot(aes(noconf_govZ_i, gap_no_gov_opposite)) +
#   geom_text_repel(aes(label = clabs)) +
#   geom_smooth(method = lm)
```

#### GDP
```{r gdp}
df_tbl %>%
  ggplot(aes(gdp_pc_10k, gap_no_gov)) +
  geom_text_repel(aes(label = clabs)) +
  geom_smooth(method = lm) +
  labs(x = "Worse Economic Performance (GDPpc)",
       y = "% Inconsistent Attitudes\nDo not agree with gov redistribution") +
  theme_classic()

# df_tbl %>%
#   ggplot(aes(gdp_pc_10k, gap_no_gov_opposite)) +
#   geom_text_repel(aes(label = clabs)) +
#   geom_smooth(method = lm)
```
## References

```{r cite}
report::cite_packages()
```


## Colophon

```{r colophon}
sessionInfo()
```