---
title: "Social Status, Liberalization and Attitudes toward Redistribution"
output: html_notebook
---

"Social Status, Liberalization and Attitudes toward Redistribution"

## ISSP, Social Inequality, Cumulation (1987, 1992, 1999 & 2009)
## ISSP, Environment, 1993, 2000 & 2010
$~$
$~$

#### **Nate Breznau, Lisa Heukamp & Hung H.V. Nguyen**
#### **University of Bremen**

_____________________________________________________________________________

$~$
$~$

Working paper available here: https://docs.google.com/document/d/1mST25rKYZ5wChRj5WyhxH_65RUa9MNR2OsO5B4-qcwY/edit#

The data cleaning is done in the file "Social Status, Liberalization and Attitudes toward Redistribution.Rmd"

# Setup


```{r, include = F}
rm(list = ls())
```


```{r setup, include=FALSE}

library(pacman)

pacman::p_load("tidyverse","knitr","haven","car","plyr","e1071","expss","stargazer","lavaan","kableExtra","MASS","glm.predict","brant", "semTools", "countrycode")

#remotes::install_github("DiogoFerrari/occupar")
#remotes::install_github("pdparker/isco88conversion")
library(occupar, isco88conversion)


wd <- "C:/data/"

# We don't want to see messages in the final document
knitr::opts_chunk$set(message = F)

#Column no missing function
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

```

Load Data
```{r}
load(paste0(wd,"socstat.Rdata"))
```


# Descriptives

## Table 1. Cases by Country-Wave

```{r tbl1, include = T, echo = T}
# Cross-tab years and countries

options(knitr.kable.NA = '')

tab1 <- df %>%
  dplyr::group_by(country, wave) %>%
  dplyr::summarize(n=n()) %>%
  spread(wave, n) %>%
  kable(., col.names = c("Country", "SI_1987", "SI_1992", "EN_1993", "SI_1999", "EN_2000", "SI_2009", "EN_2010"), caption = "Country Sample Size by Wave, ISSP 'Social Inequality (SI) & Environment (EN)", format.args = list(big.mark = ","))


kable_styling(tab1)



```



## Table 2. Descriptive Statistics

Final coding of variable 'wrkst'
1 Employed, full-time
2 Employed, part-time
3 Employed, less than part-time
5 Unemployed
6 Student, school, vocational training
7 Retired
8 Housewife,-man, home duties or Helping family member
9 Permanently disabled
10 Other, not in labour force, or refused, don't know, no answer


```{r tbl2, echo = T}
tab2 <- dplyr::as.tbl(dplyr::select(df, year, ageC, female, educyrs, degree, child, married, rincZ, hincZ, isei, egp, egp6, union, sparent, wrkhrs, wrkst, reduce))

# make categories out of categorical variables
tab2 <- tab2 %>%
  mutate(egp_un = as.numeric(egp6 == "Unskilled"),
         egp_skl = as.numeric(egp6 == "Skilled"),
         egp_othr = as.numeric(egp6 == "Self"),
         egp_rou = as.numeric(egp6 == "Routine"),
         egp_svc2 = as.numeric(egp6 == "Service II"),
         egp_svc1 = as.numeric(egp6 == "Service I"),
         wk_full = as.numeric(wrkst == 1),
         wk_part = as.numeric(wrkst == 2),
         wk_lesspart = as.numeric(wrkst == 3),
         wk_unemp = as.numeric(wrkst == 5),
         wk_school = as.numeric(wrkst == 6),
         wk_retired = as.numeric(wrkst == 7),
         wk_home = as.numeric(wrkst == 8),
         wk_disab = as.numeric(wrkst == 9),
         wk_other = as.numeric(wrkst == 10))

tab2 <- dplyr::select(tab2, year, ageC, female, educyrs, child, married, rincZ, hincZ, isei, egp_un, egp_skl, egp_othr, egp_rou, egp_svc2, egp_svc1, wk_full:wk_other, wrkhrs, union, sparent, reduce)

# Get summary stats
tab2_1 <- summarise_all(tab2, list(mean), na.rm = T)
tab2_1.1 <- summarise_all(tab2, list(sd), na.rm = T)
tab2_2 <- summarise_all(tab2, list(min), na.rm = T)
tab2_3 <- summarise_all(tab2, list(max), na.rm = T)
tab2_4 <- summarise_all(tab2, funs(sum(!is.na(.))))

# Transpose into columns
tab2_1 <- as.data.frame(t(round(tab2_1, 2)))
tab2_1.1 <- as.data.frame(t(round(tab2_1.1, 2)))
tab2_2 <- as.data.frame(t(round(tab2_2, 0)))
tab2_3 <- as.data.frame(t(tab2_3))
tab2_4 <- as.data.frame(t(tab2_4))
tab2_0 <- as.data.frame(c("Year","Age, in years", "Female", "Education, in years", "Children", "Married", "Indiv. Earnings, country-Z", "Household Earnings, country-Z", "Occ. Status, ISEI", "EGP - Unskilled", "EGP - Skilled", "EGP - Self/Other", "EGP - Routine", "EGP - Service II", "EGP - Service I", "Work - Full-time", "Work - Part-Time", "Work - Less-part-time", "Work - Unemployed", "Work - School/Training", "Work - Retired", "Work - Homecare/Family help", "Work - Disabled", "Work - Other/NA", "Hours Worked", "Union", "Parent", "DV - Support Redistribution"))


# Bind into table

tab2f <- cbind(tab2_0,tab2_1,tab2_1.1,tab2_2,tab2_3,tab2_4)
colnames(tab2f) <- c("Variable","Mean","SD","Min","Max","N")

tab2f <- kable(tab2f)

kable_styling(tab2f)

rm(tab2_0, tab2_1, tab2_1.1, tab2_2, tab2_3, tab2_4)

```

## Fig 1. Scatterplot of Preferences for Redistribution

```{r fig1, echo = T}

```


## Table 3. Correlations, Pooled

```{r corrs}
tab2 <- dplyr::select(tab2, reduce, everything())
cor1 <- cor(tab2, use = "pairwise.complete.obs")
cor1k <- kable(cor1, digits = 2)
kable_styling(cor1k)

# check that correlations look 'right'
```














## New ideal types 

```{r ideal, include = FALSE}
df <- df %>%
  mutate(
    itype = case_when(
      egp6 == "Routine" & female == 0 ~ 1,
      (egp6 == "Unskilled" | egp6 == "Routine") & incZ < -1 ~ 2,
      
    )
  )
```

## Data analysis
```{r analysis, include = FALSE}
df <- df %>% 
  group_by(cntry)
df$incdiff <- dplyr::recode(df$incdiff, `8` = NA_real_, `9` = NA_real_) # 8 = NA or should be kept?

df_lw <- df[complete.cases(df$incdiff),]
df_lw <- df_lw[complete.cases(df_lw$cntry),]


df_lw$f_incdiff <- as.factor(df_lw$incdiff)
df_lw$o_incdiff <- as.ordered(df_lw$incdiff)


ggplot(df_lw, aes(f_incdiff)) +
  geom_bar(fill = "gray40") + 
  scale_x_discrete("Original Response Choices (non-response omitted)", labels = c("Strongly disagree","Disagree","Neutral","Agree" ,"Strongly agree")) + 
  ggtitle("Reduce income differences")



## Ordered logit 

mod1 <- polr(f_incdiff ~ age*age + female + educyrs + degree + child + married + incZ + egp6 + as.factor(cntry), data = df_lw)

```




































## Construct the measurement model

```{r mm, include = FALSE}
## Data preparations
# New variables with unique names
df <- df %>%
  mutate(
    incd = v33, 
    jobs = v35,
    basicinc = v38,
    diff2large = v32,
  )


# Listwise deletion


df_lw <- df[complete.cases(df$incd),]
df_lw <- df_lw[complete.cases(df_lw$jobs),]
df_lw <- df_lw[complete.cases(df_lw$basicinc),]
df_lw <- df_lw[complete.cases(df_lw$cntry),]
df_lw <- df_lw[complete.cases(df_lw$diff2large),]
# Can use str or summary as well

table(df$incd) 
table(df$jobs) # last two waves: no data
table(df$basicinc) # last two waves: no data


# Creating factor variables & ordered variables
df_lw$f_incd <- as.factor(df_lw$incd)
df_lw$f_jobs <- as.factor(df_lw$jobs)
df_lw$f_basicinc <- as.factor(df_lw$basicinc)

df_lw$o_incd <- as.ordered(df_lw$incd)
df_lw$o_jobs <- as.ordered(df_lw$jobs)
df_lw$o_basicinc <- as.ordered(df_lw$basicinc)

# Plots: checking the normality of questions. ALl three are skewed.



ggplot(df_lw, aes(f_incd)) +
  geom_bar(fill = "gray40") + 
  scale_x_discrete("Original Response Choices (non-response omitted)", labels = c("Strongly disagree","Disagree","Neutral","Agree" ,"Strongly agree","Can't choose")) + 
  ggtitle("Provide Jobs for Everyone who Wants One")

ggplot(df_lw, aes(f_jobs)) +
  geom_bar(fill = "gray40") + 
  scale_x_discrete("Original Response Choices (non-response omitted)", labels = c("Strongly disagree","Disagree","Neutral","Agree" ,"Strongly agree","Can't choose")) + 
  ggtitle("Provide Jobs for Everyone who Wants One")

ggplot(df_lw, aes(f_basicinc)) +
  geom_bar(fill = "gray40") + 
  scale_x_discrete("Original Response Choices (non-response omitted)", labels = c("Strongly disagree","Disagree","Neutral","Agree" ,"Strongly agree","Can't choose")) + 
  ggtitle("Provide Jobs for Everyone who Wants One")

#More normality tests (package e1071)

e1071::skewness(df_lw$incd)
e1071::skewness(df_lw$jobs)
e1071::skewness(df_lw$basicinc)

# ks.test(df_lw$incd, y='pnorm',alternative='two.sided')

## Constructing the latent variable with lavaan

# Confirmatory factor analysis - models

mod1 <- ' att =~ incd + diff2large'
fit1 <- cfa(mod1, data = df_lw) # default setting.

summary(fit1, fit.measures =TRUE, standardized = TRUE)
inspect(fit1,what="std")$lambda

mod2 <- ' att =~ 1*incd + 1*jobs + 1*basicinc'
fit2 <- cfa(mod2, data = df_lw) # fixed at 1, Figure 2B Schoot, Lugtig & Hox 2012

summary(fit2)
inspect(fit2,what="std")$lambda


# Testing measurement invariance across social groups 



#mi1 <- measEq.syntax(fit1)
summary(fit1)

```


